\documentstyle[11pt,fancyheadings]{article}


\addtolength{\textheight}{1.5in}
\setlength{\voffset}{-0.5in}
\addtolength{\textwidth}{1in}
\setlength{\hoffset}{-0.5in}

\pagestyle{empty}
\parindent=0.0cm
\parskip=0.25cm

\newcommand{\etal}{{\it et.~al.}}
\newcommand{\remember}[1]{{\bf Remember: \{#1\}}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center} 
{\Large\bf John E. Jacobsen}\\[0.3cm]
{\bf\Large Curriculum Vitae}
\end{center}
\vspace{1.0cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\bf Contact Information:}
%\vspace{0.10cm}

\begin{center}
\begin{tabular}[t]{ll}

Address:   & NPX Designs, Inc. \\
	   & 5341 S. Cornell Ave., Suite 3 \\
	   & Chicago, Illinois 60615 USA\\[0.25cm]

Phone: & (773) 208 0380 (voice) \\
       & (206) 338-2099 (FAX)\\[0.25cm]

Email: & {\tt john@mail.npxdesigns.com}\\
Web Site: & {\tt http://npxdesigns.com }\\
GitHub: & {\tt http://github.com/eigenhombre }\\
Blog: & {\tt http://eigenhombre.com }

\end{tabular}
\end{center}

\vspace{0.5cm}

{\bf Overview:}

With over two decades of experience in high energy physics and particle astrophysics, I am a software engineer specializing in experimental physics and other high-performance computing environments.  My recent work for the IceCube Neutrino Observatory at the South Pole includes several critical components of the detector's data acquisition system and an innovative, end-to-end implementation of the experiment control system, in production since early 2009.  I also play a key role in troubleshooting and maintaining that detector during calibration and normal operations (\textgreater 99\% uptime).

It is a passion of mine to address difficult computing problems in science, problems which may engage multiple challenges in terms of computability, complexity, scalability, and usability.  I am particularly interested in using modern, high-level programming languages (such as Python, Clojure, and other functional languages), to create simple, beautiful, usable and powerful systems for the collection, analysis and visualization of data on the frontiers of science.

\vspace{0.5cm}

{\bf Education:}
\vspace{0.25cm}

\begin{tabular}[t]{lp{0.800\textwidth}}

December, 1996: & Ph.~D., Department of Physics,
University of Wisconsin -- Madison.
\\[0.25cm]

1993--1996: & Graduate Student, Department of Physics, and Department of Art,
University of Wisconsin -- Madison.\\[0.25cm]

1991--1993: & Department of Art, University of Wisconsin -- Madison.
\\[0.25cm]

1990: & B.S., Physics, University of Wisconsin -- Madison.  Graduated
with distinction, class rank 17 out of 3073.

\end{tabular}

\newpage
\pagestyle{myheadings}
\markright{\bf J.~E. Jacobsen}

{\bf Positions Held:}
\vspace{0.25cm}

\begin{tabular}[t]{lp{0.800\textwidth}}

2004--present: & President, NPX Designs, Inc.\\[0.1cm]
                            & Current and recent clients include: \\
                            & The University of Wisconsin, Madison (IceCube Project);\\
                            & The University of Maryland, Dept. of Physics;\\
                            & The Pennsylvania State University, Dept. of Physics;\\
                            & E.~O.~Lawrence Berkeley National Laboratory, Berkeley, CA;\\
                            & Pragma Securities, Inc., New York, NY\\[0.25cm]

2002--2004: & Sole Proprietor, John Jacobsen IT Services, Chicago, IL\\[0.25cm]

1998--2002: & Computer Systems Engineer, E.~O.~Lawrence Berkeley National Laboratory, Berkeley, CA\\[0.25cm]

1997--1998: & Postdoctoral Research Associate,
Department of Physics, University of Wisconsin, Madison,
Wisconsin\\[0.25cm]

1997--present: & Visiting Scholar,
Department of Physics, University of California, Berkeley,
California\\[0.25cm]

1998--present: & Postdoctoral Guest Researcher,
E.~O.~Lawrence Berkeley National Laboratory,
Berkeley, California\\[0.25cm]

1994--1996: & Graduate Research Assistant, 
Department of Physics, University of Wisconsin, Madison,
Wisconsin\\[0.25cm]

1993--1994: & United States Department of Education Fellow, Department
of Physics, University of Wisconsin, Madison,
Wisconsin\\[0.25cm]

1991--1993: & Undergraduate Physics Research Assistant, Department
of Physics, University of Wisconsin, Madison,
Wisconsin\\[0.25cm]

1990--1991: & Physics Research Assistant, CERN, Geneva, Switzerland
\\[0.25cm]

1987--1990: & Undergraduate Physics Research Assistant, Department
of Physics, University of Wisconsin, Madison,
Wisconsin\\[0.25cm]

\end{tabular}

{\bf Recent Conferences:}
\vspace{0.25cm}

\begin{tabular}[t]{lp{0.800\textwidth}}

2012: & {\bf Clojure/conj}, Raleigh, NC\\
2012: & {\bf Clojure/West}, San Jose, CA\\
2010: & {\bf O'Reilly Open Source Conference}, Portland, OR\\
2008: & {\bf O'Reilly Open Source Conference}, Portland, OR\\
2008: & {\bf PyCon}, Chicago, IL\\
\end{tabular}

\newpage

{\bf Selected Awards and Honors:}
\vspace{0.25cm}

\begin{tabular}[t]{lp{0.800\textwidth}}

1994: & Emanuelle A. Piori Award (highest score on graduate qualifying exam).
University of Wisconsin -- Madison Department of Physics.\\[0.25cm]

1993-1994: & U.~S.~Department of Education Graduate Fellowship.  
University of Wisconsin -- Madison Department of Physics.\\[0.25cm]

1990: & Albert Radtke Scholarship (outstanding undergraduate physics major).
University of Wisconsin -- Madison Department of Physics.\\[0.25cm]

\end{tabular}

{\bf Ph.D. Thesis:}

``Simulating the Detection of Muons and Neutrinos in Deep Antarctic Ice.'' The University of Wisconsin -- Madison (1996).  URL: {\tt http://johnj.com/thesis}
\vspace{0.25cm}

{\bf Publications in Refereed Journals:}\footnote{Updated 2012}

\begin{enumerate}

\item ``Search for Excited Neutrinos in $Z$ Decays'' (with the ALEPH
  Collaboration, D.~Decamp et.~al.), Phys.~Lett.~{\bf B250} 172-182
  (1990).

\item ``Measurement of Electroweak Parameters from $Z$ Decays into
  Fermion Pairs'' (with the ALEPH Collaboration, D.~Decamp et.~al.),
  Z.~Phys.~{\bf C48} 365-392 (1990).

\item ``Using Neural Networks with Jet Shapes to Identify $b$ jets in
  $e^+ e^-$ Interactions'' (with L.~Bellantoni, J.~Conway, Y.~Pan and
  S.~L.~Wu), Nucl.~Instrum.~Meth. {\bf A310} 618-622 (1991).

\item ``Measurement of the Strong Coupling Constant $\alpha_S$ from
  Global Event Shape Variables of Hadronic $Z$ Decays'' (with the
  ALEPH Collaboration, D.~Decamp et.~al.), Phys.~Lett. {\bf B255}
  623-633 (1991).

\item ``Measurement of $B - \bar B$ Mixing at the $Z$'' (with the
  ALEPH Collaboration, D.~Decamp et.~al.), Phys.~Lett.~{\bf B258}
  236-246 (1991).

\item ``Measurement of the $B$ Hadron Lifetime'' (with the ALEPH
  Collaboration, D.~Decamp et.~al.), Phys.~Lett.~{\bf B257} 492-504
  (1991).

\item ``Measurement of Charge Asymmetry in Hadronic $Z$ Decays'' (with
  the ALEPH Collaboration, D.~Decamp et.~al.), Phys.~Lett.~{\bf B259}
  377-388 (1991).

\item ``Search for a New Weakly Interacting Particle'' (with the ALEPH
  Collaboration, D.~Decamp et.~al.), Phys.~Lett.~{\bf B262} 139-147
  (1991).

\item ``Charged Particle Pair Production Associated with a Lepton Pair
  in $Z$ Decays: Indication of an Excess in the Tau Channel'' (with
  the ALEPH Collaboration, D.~Decamp et.~al.), Phys.~Lett.~{\bf B263}
  112-122 (1991).

\item ``Measurement of the Forward-Backward Asymmetry in $Z
  \rightarrow b \bar b$ and $Z \rightarrow c \bar c$'' (with the ALEPH
  Collaboration, D.~Decamp et.~al.), Phys.~Lett.~{\bf B263} 325-336
  (1991).

\item ``Measurement of the Charged Particle Multiplicity Distribution
  in Hadronic $Z$ Decays'' (with the ALEPH Collaboration, D.~Decamp
  et.~al.), Phys.~Lett.~{\bf B273} 181-192 (1991).

\item ``Measurement of the Polarization of $\tau$ Leptons Produced in
  $Z$ Decays'' (with the ALEPH Collaboration, D.~Decamp et.~al.),
  Phys.~Lett.~{\bf B265} 430-444 (1991).

\item ``Measurement of Isolated Photon Production in Hadronic $Z$
  Decays'' (with the ALEPH Collaboration, D.~Decamp et.~al.),
  Phys.~Lett.~{\bf B264} 476-486 (1991).

\item ``Measurement of the Absolute Luminosity with the ALEPH
  Detector'' (with the ALEPH Collaboration, D.~Decamp et.~al.),
  Z.~Phys.~{\bf C53} 375-390 (1992).

\item ``Searches for New Particles in $Z$ Decays Using the ALEPH
  Detector'' (with the ALEPH Collaboration, D.~Decamp et.~al.),
  Phys.~Rept.~{\bf 273} 253-340 (1992).

\item ``Improved Measurements of Electroweak Parameters from $Z$
  Decays Into Fermion Pairs'' (with the ALEPH Collaboration, D.~Decamp
  et.~al.), Z.~Phys.~{\bf C53} 1-20 (1992).

\item ``An Investigation Into Intermittency'' (with the ALEPH
  Collaboration, D.~Decamp et.~al.), Z.~Phys.~{\bf C53} 21-32 (1992).

\item ``Possibility that High-Energy Neutrino Telescopes Could Detect
  Supernovae'' (with F.~Halzen and E.~Zas), Phys. Rev. {\bf D49}, n4,
  p.~1758 (1994).

\item ``First Data and Future Prospects for AMANDA, the Antarctic Muon
  and Neutrino Detector Array'' (with P.~Askebjer \etal), Antarctic
  Journal {\bf 24} \, 337 (1994).

\item ``Optical Properties of the South Pole Ice at Depths Between 0.8
  and 1 Kilometer'' (with P.~Askebjer \etal), Science, Vol.~267,
  p.~1147 (1995)

\item ``On the Age vs.~ Depth and Optical Clarity of Deep Ice at South
  Pole'' (with AMANDA collaboration, P.~Askebjer \etal), Journal of
  Glaciology, Vol.~41, No.~139 (1995).

\item ``Ultratransparent Ice as a Supernova Detector'' (with F.~Halzen
  and E.~Zas), Phys.~Rev. {\bf D53}, n12, p.~7359 (1996).

\item ``UV and Optical Light Transmission Properties in Deep Ice at
  the South Pole'' (with the AMANDA collaboration, P. Askebjer {\sl et
    al.}), Geophysical Research Letters {\bf 24}, 11, 1355 (1997).

\item ``Optical Properties of Deep Ice at the South Pole -
  Absorption'' (with the AMANDA collaboration (P.~Askebjer {\sl et
    al.}), Applied Optics {\bf 36}, 18, 4168 (1997).

\item The AMANDA Neutrino Telescope: Principle of Operation and First
  Results (the AMANDA Collaboration, E. Andres et al.), DESY-99-073
  (Jun 1999). 36pp. Astropart. Phys. {\bf 13} 1-20 (2000).  e-Print
  Archive: astro-ph/9906203.

\item Observation of High-Energy Neutrinos Using Cerenkov Detectors
  Embedded Deep in Antarctic Ice.  The AMANDA Collaboration
  (E. Andres, et al.), Nature {\bf 410} 441-443 (2001).

\item Search for Point Sources of High Energy Neutrinos with AMANDA
  (the AMANDA Collaboration, J. Ahrens et al.) (Aug
  2002). 46pp. Submitted to Astrophys. J. (2002) e-Print Archive:
  astro-ph/0208006.

\item Observation Of High-Energy Atmospheric Neutrinos With The
  Antarctic Muon And Neutrino Detector Array.  The AMANDA
  Collaboration (J. Ahrens et al.) (May 2002). 21pp. Phys. Rev. {\bf
    D66} 012005 (2002).  e-Print Archive: astro-ph/0205109.

\item Limits To The Muon Flux From Wimp Annihilation In The Center Of
  The Earth With The AMANDA Detector (by the AMANDA Collaboration,
  J. Ahrens et al.) (Feb 2002). 13pp. Phys. Rev. {\bf D66} 032006
  (2002). e-Print Archive: astro-ph/0202370.

\item Search For Supernova Neutrino Bursts With The AMANDA Detector
  (the AMANDA Collaboration, J. Ahrens et al.) (May 2001). 20pp.
  Astropart. Phys. {\bf 16} 345-359 (2002).  e-Print Archive:
  astro-ph/0105460.

\item Results from AMANDA (by the AMANDA Collaboration, C. Wiebusch et
  al.).  19pp.  Modern Physics Letters {\bf A 17}, 31 2019-2037
  (2002).

\item Search For Neutrino-Induced Cascades With the AMANDA Detector
  (the AMANDA Collaboration, J. Ahrens et al.).  Physical Review {\bf
  D67} 012003 (2003).

\item Limits on Diffuse Fluxes of High-energy Extraterrestrial
  Neutrinos with the AMANDA-B10 Detector (J. Ahrens et al.).
  Phys. Rev. Lett. {\bf 90} 251101 (2003).

\item Sensitivity of the IceCube Detector to Astrophysical Sources of
  High Energy Muon Neutrinos (with the IceCube Collaboration,
  J. Ahrens et al.).  Astropart. Phys. {\bf 20} 507-532 (2004).

\item Muon Track Reconstruction and Data Selection Techniques in
  AMANDA (with the AMANDA Collaboration, J. Ahrens et al.).
  Nucl. Instrum. Meth. {\bf A524} 169-194 (2004).

\item Search for Extraterrestrial Point Sources of Neutrinos with
  AMANDA-II (with the AMANDA Collaboration, J. Ahrens et al.).
  Phys. Rev. Lett. {\bf 92} 071102 (2004).

\item Measurement of the Cosmic Ray Composition at the Knee with the
  SPASE-2/AMANDA-B10 Detectors (with the AMANDA and SPASE
  Collaborations, J. Ahrens et al.).  Astropart. Phys. {\bf 21}
  565-581 (2004).

\item Calibration and Survey of AMANDA with the SPASE Detectors (with
  the SPASE and AMANDA Collaborations, J. Ahrens et al.).
  Nucl. Instrum. Meth. {\bf A522} 347-359 (2004).

\item Search for Neutrino-induced Cascades with AMANDA (with the
  AMANDA Collaboration, M. Ackermann et al.).  Astropart. Phys. {\bf
    22} 127-138 (2004).

\item Search for Extraterrestrial Point Sources of High Energy
  Neutrinos with AMANDA-II Using Data Collected in 2000-2002 (with the
  AMANDA Collaboration, M. Ackermann et al.).  Phys. Rev. {\bf D71}
  077102 (2005).

\item Neutrino Astronomy and Cosmic Rays at the South Pole: Latest
  Results from AMANDA and Perspectives for IceCube (with the AMANDA
  and IceCube Collaborations, P. Desiati et al.).  Prepared for 19th
  European Cosmic Ray Symposium (ECRS 2004), Florence, Italy (30 Aug -
  3 Sep 2004).  Int. J. Mod. Phys. {\bf A20} 6919-6923 (2005).

\item New Results from the AMANDA Neutrino Telescope (with the AMANDA
  Collaboration, M. Ackermann et al.).  Nucl. Phys. Proc. Suppl. {\bf
    145} 319-322 (2005). Also in Conca Specchiulla 2004, Neutrino
  oscillation 319-322.

\item Flux Limits on Ultra High Energy Neutrinos with AMANDA-B10
  (M. Ackermann et al.).  Astropart. Phys. {\bf 22} 339-353 (2005).

\item Limits on the Muon Flux from Neutralino Annihilations at the
  Center of the Earth with AMANDA (with the AMANDA collaboration,
  A. Achterberg et al.).  Astropart. Phys. {\bf 26} 129-139 (2006).

\item The ICECUBE Prototype String in AMANDA (with the AMANDA
  collaboration, M. Ackermann et al.).  Nucl. Instrum. Meth. {\bf
    A556} 169-181 (2006).

\item First Year Performance of The IceCube Neutrino Telescope (with
  the IceCube collaboration, A. Achterberg et al.).
  Astropart. Phys. {\bf 26} 155-173 (2006).

\item Limits on the High-energy Gamma and Neutrino Fluxes from the SGR
  1806-20 Giant Flare of December 27th, 2004 with the AMANDA-II
  Detector (with the IceCube collaboration, A. Achterberg et al.).
  Phys. Rev. Lett. {\bf 97} 221101 (2006).

\item On the Selection of AGN Neutrino Source Candidates for a Source
  Stacking Analysis with Neutrino Telescopes (with the IceCube
  collaboration, A. Achterberg et al.).  Astropart. Phys. {\bf 26}
  282-300 (2006).

\item Astroparticle physics with high energy neutrinos: from AMANDA to
  IceCube (F. Halzen et al.).  The European Physical Journal {\bf C} -
  Particles and Fields (2006).  21pp.  10.1140/epjc/s2006-02536-4.

\item Five Years of Searches for Point Sources of Astrophysical
  Neutrinos with the AMANDA-II Neutrino Telescope (with the IceCube
  collaboration, A. Achterberg et al.).  Phys. Rev. {\bf D75} 102001
  (2007).

\item Detection of Atmospheric Muon Neutrinos with the IcCube 9-String
  Detector (with the IceCube Collaboration, A.  Achterberg et al.),
  Phys. Rev. {\bf D76} 027901 (2007).

\item Multiyear Search for a Diffuse Flux of Muon Neutrinos with
  AMANDA-II (with the IceCube Collaboration, A.  Achterberg et al.),
  Phys. Rev. {\bf D76} 042008 (2007).

\item Search for Ultra-High Energy Neutrinos with AMANDA-II (with the
  IceCube Collaboration, M. Ackermann et al.), preprint
  arXiv:0711.3022, to appear in Astrophys. J (2007).

\item The Search for Muon Neutrinos from Northern Hemisphere Gamma-Ray
  Bursts with AMANDA (with the IceCube Collaboration, M. Ackermann et
  al.), preprint arXiv:0705.1186, to appear in Astrophys. J (2007).

\item Search for Neutrino-Induced Cascades from Gamma-Ray Bursts with
  AMANDA (with the IceCube Collaboration, A. Achterberg et al.),
  Astrophys.J. 664, 397 (2007).

\item Five Years of Searches for Point Sources of Astrophysical
  Neutrinos with the AMANDA-II Neutrino Telescope (with the IceCube
  Collaboration, A. Achterberg et al.), Phys.Rev. {\bf D75} 102001
  (2007).

\item Search for ultra high-energy neutrinos with AMANDA-II
  (M. Ackermann et al.), Astrophysical Journal, {\bf 675}, 1014
  (2008).

\item The Search for Muon Neutrinos from Northern Hemisphere Gamma-Ray
  bursts with AMANDA (A. Achterberg et al.), Astrophysical Journal,
  {\bf 674}, 357 (2008).

\item Limits on a Muon Flux from Neutralino Annihilations in the Sun
  with the IceCube 22-String Detector, R. Abbassi et al.,
  Phys. Rev. Lett. 102, 201302 (2009).

\item "Determination of the atmospheric neutrino flux and searches for
  new physics with AMANDA- II", R. abbassi et al., Phys. Rev. {\bf
    D79}, 102005 (2009).

\item Solar Energetic Particle Spectrum on 13 December 2006 Determined
  by IceTop,” R. Abassi et al., Astrophysical J. Lett. {\bf 689}, L65
  (2008).

\item Search for Point Sources of High Energy Neutrinos with Final
  Data from AMANDA-II,” R. Abassi et al., Phys. Rev. {\bf D79}, 062001
  (2009).

\item Search for High-Energy Muon Neutrinos from the 'Naked-Eye' GRB
  080319B with the IceCube Neutrino Telescope,” R. Abassi et al.,
  Astrophysical Journal 701 (2009) 1721-1731, {\bf DOI}:
  10.1088/0004-637X/701/2/1721.

\item First Neutrino Point-Source Results From the 22-String IceCube
  Detector,” R. Abassi et al., preprint arXiv:0905.2253.

\item Measurement of sound speed vs. depth in South Pole ice: pressure
  and shear waves,” R. Abassi et al., submitted to Journal of
  Geophysical Research.

\item "Extending the Search for Neutrino Point Sources with IceCube
  above the Horizon," R. Abbasi et al (IceCube Collaboration),
  Phys. Rev. Lett. {\bf 103}, 221102 (2009) DOI:10.1103
  arXiv:0911.2338 [astro-ph.HE].

\item The IceCube Data Acquisition System: Signal Capture,
  Digitization, and Timestamping. R. Abbassi et al., LBNL-1668E,
  Nuclear Instruments and Methods {\bf A601}, 294 (2009).

\end{enumerate}

{\bf Selected Presentations:}
\vspace{0.25cm}

\begin{tabular}[t]{p{0.950\textwidth}}

``Searching for Neutrinos using Open Source at the Bottom of the
  World'' (with K. Beattie and D. Glowacki), at the O'Reilly Open
  Source Conference, Portland, Oregon, July 25, 2008\\ ({\tt
    http://en.oreilly.com/oscon2008/public/schedule/detail/2614}).\\[0.25cm]

``Data Analysis and Simulation Software for the AMANDA Experiment.''
  IceCube Workshop, University of California -- Irvine, 27 March,
  1998.\\[0.25cm]

``The AMANDA Experiment at South Pole.''  Yerkes Observatory, Williams
  Bay, Wisconsin, 10 June 1996.\\[0.25cm]

``Particle Physics on Ice: The Antarctic Muon and Neutrino Detector
  Array.''  University of Pennsylvania, Rutgers University, Princeton
  University, 21-23 May 1996.\\[0.25cm]

``A New High-Energy Window on the Heavens\ldots AMANDA.''  Cornell
  University, 18 June 1993.\\[0.25cm]

``Using Neural Networks for $b$-Jet Identification.''  ALEPH
  Collaboration, CERN, Geneva, Switzerland, 23 Oct.~1990.\\[0.25cm]



\end{tabular}
\vspace{0.25cm}

{\bf Preprints and Publications in Conference  Proceedings:}\footnote{Updated 2012}
\vspace{0.25cm}

\begin{enumerate}
\item VHE Gamma Ray Studies at the Haleakala Gamma Ray Observatory
  (with L.~Resvanis \etal), Nucl. Phys. B, Proc. Suppl. 14A,
  pp. 205-210 (1989).

\item Searches for the Standard Higgs Boson Produced in the Reaction
  ${e^+}{e^-} \rightarrow H^0 Z^*$ (with the ALEPH Collaboration,
  D.~Decamp \etal), Contribution to the Aspen, La Thuile and Moriond
  Conferences (Winter 1991).

\item Transparency of Antarctic Ice: First Results (with AMANDA
  collaboration, S.~Barwick \etal), {\it The Workshop on Astrophysics
    of High Energy Neutrinos}, Honolulu, Hawaii (1992).

\item Antarctic Muon and Neutrino Detector Array (with AMANDA
  collaboration, S.~Barwick \etal), {\it Proceedings of the 2nd UCLA
    International Conference on Gamma Ray and Neutrino Cosmology}, Los
  Angeles, California (1992).

\item AMANDA: South Pole Neutrino Detector (with AMANDA collaboration,
  S.~Barwick \etal), {\it Proceedings of the XXVIth International
    Conference on High Energy Physics (ICHEP 92)}, Dallas, Texas
  (1992).

\item AMANDA: Design of a 1 Kilometer Deep High Energy Neutrino
  Telescope (with AMANDA collaboration, S.~Tilav \etal), {\it
    Proceedings of the XXIIIrd International Cosmic Ray Conference},
  Calgary, Canada (1993).

\item Surface/Under Ice Muon Coincidences at the South Pole (with
  S.~Tilav \etal), {\it Proceedings of the XXIIIrd International
    Cosmic Ray Conference}, Calgary, Canada (1993).

\item AMANDA: Measurement of South Pole Ice Transparency at 800 Meter
  Depth (with AMANDA collaboration, T.~Miller \etal), {\it Proceedings
    of the XXIIIrd International Cosmic Ray Conference}, Calgary,
  Canada (1993).

\item Hardware Design and Prototype Tests of the AMANDA Neutrino
  Detector (with AMANDA collaboration, D.~Lowder \etal), {\it
    Proceedings of the XXIIIrd International Cosmic Ray Conference},
  Calgary, Canada (1993).

\item Ultra High Energy Neutrino Astrophysics with AMANDA (with AMANDA
  Collaboration, P.~B.~Price \etal), {\it Proceedings of the
    International Conference on Non-Accelerator Particle Physics},
  Bangalore, India (1994).

\item The Indirect Detection of Halo Dark Matter (with F.~Halzen).
  {\it Proceedings of the International Conference on Critique of the
    Sources of Dark Matter in the Universe}, UCLA, Los Angeles,
  California (1994).

\item Antarctic Muon and Neutrino Detector: First Data and Outlook
  (with John Lynch and the AMANDA Collaboration), {\it Proceedings of
  the Rpobotic Telescopes Conference, Astronomical Society of the
  Pacific}, Flagstaff, Arizona (1994).

\item AMANDA: Status Report from the 1993-94 Campaign and Optical
  Properties of the South Pole Ice (with AMANDA Collaboration,
  P.~Askebjer \etal), To appear in the {\it Proceedings of the XVI
    International Conference on Neutrino Physics and Astrophysics},
  Eilat, Israel (1994).

\item The Detection of Cold Dark Matter with Neutrino Telescopes (with
  F.~Halzen), University of Wisconsin Preprint MAD-PH-838.  {\it
    Proceedings of the 16th Annual Montreal-Rochester-Syracuse-Toronto
    Meeting on High Energy Physics: What Next? Exploring the Future of
    High Energy Physics}, Montreal, Canada (1994).

\item Initial Analysis of Coincident Events Between the SPASE and
  AMANDA Detectors (with T.~Miller \etal), {\it Nuclear Physics B,
    Proc. Supp.} {\bf 43}, 245 (1995).

\item Ultra-transparent Antarctic Ice as a Supernova Detector (with
  F.~Halzen and E.~Zas), {\it Proceedings of the XXIVth International
    Cosmic Ray Conference}, Rome, Italy (1995).

\item A System to Search for Supernova Bursts with the AMANDA Detector
  (with AMANDA collaboration, R.~Wischnewski \etal), {\it Proceedings
  of the XXIVth International Cosmic Ray Conference}, Rome, Italy
  (1995), Vol.~1, p.~658.

\item Status and Capabilities of AMANDA-94 (with AMANDA collaboration,
  P.~Mock \etal), {\it Proceedings of the XXIVth International Cosmic
    Ray Conference}, Rome, Italy (1995), Vol.~1, p.~758.

\item Measurements of the Absorption Length of the Ice at the South
  Pole in the Wavelength Interval 410 nm to 610 nm (with AMANDA
  collaboration, B.~Erlandsson \etal), {\it Proceedings of the XXIVth
    International Cosmic Ray Conference}, Rome, Italy (1995), Vol.~1,
  p.~1039.

\item The Design of a Neutrino Telescope using Natural Deep Ice as a
  Particle Detector (with AMANDA collaboration, L.~Gray \etal), {\it
    Proceedings of the XXIVth International Cosmic Ray Conference},
  Rome, Italy, 1995), Vol.~1, p.~816.

\item Indirect Evidence for Long Absorption Lengths in Antarctic Ice
  (with AMANDA collaboration, S.~Tilav \etal), {\it Proceedings of the
  XXIVth International Cosmic Ray Conference}, Rome, Italy (1995),
  Vol.~1, p.~1011.

\item Optical Properties of South Pole Ice for Neutrino Astrophysics
  (with AMANDA collaboration, P.~B.~Price \etal), {\it Proceedings of
  the XXIVth International Cosmic Ray Conference}, Rome, Italy (1995),
  Vol.~1, p.~777.

\item SPASE-AMANDA Coincidences at the South Pole (with T.~Miller
  \etal), {\it Proceedings of the XXIVth International Cosmic Ray
    Conference}, Rome, Italy (1995), Vol.~2, p.~768.

\item Remote Surveys of AMANDA (with R.~Porrata \etal), {\it
  Proceedings of the XXIVth International Cosmic Ray Conference},
  Rome, Italy (1995), Vol.~1, p.~1009.

\item Using Extra-clear Antarctic Ice as a Supernova Detector (with
  F.~Halzen and E.~Zas).  {\it Proceedings of the XXIVth International
    Cosmic Ray Conference}, Rome, Italy (1995), Vol.~1, p.~1027.

\item 1995-96 Results for the AMANDA Neutrino Observatory, (with the
  AMANDA Collaboration, P.~B.~Price \etal), {\it Proceedings of the
    $7^{th}$ International Workshop on Neutrino Telescopes}, p.383,
  Venice, Italy (1996).

\item 1995-1996 Results for the AMANDA Neutrino Observatory (with
  P.~Askebjer \etal), {\it Proceedings of the International Workshop
    on Future Prospects of Baryon Instability Search}, Oak Ridge
  National Laboratory (1996), Yu.~Kamyshkov, ed.

\item The AMANDA Experiment (with the AMANDA Collaboration,
  P.~O.~Hulth \etal), {\it Proceedings of the $17^{th}$ International
    Conference on Neutrino Physics and Astrophysics (Neutrino 96)},
  p.518, Helsinki, Finland (1996).

\item Status of the AMANDA South Pole Neutrino Detector (with the
  AMANDA collaboration, F. Halzen \etal), {\it Proceedings of the
    International Workshop on Aspects of Dark Matter in Astrophysics
    and Particle Physics}, Heidelberg, Germany (1996).

\item 1995-96 Results for the AMANDA Neutrino Observatory (with the
  AMANDA Collaboration, P.~B.~Price \etal), {\it Proceedings of the
    $7^{th}$ International Workshop on Neutrino Telescopes}, p.383,
  Venice, Italy (1996).

\item Latest Results from AMANDA (with the AMANDA collaboration,
  P.B. Price \etal), in {\it Proc. XXXIInd Rencontres de Moriond
    (``Very High Energy Phenomena in the Universe'')}, Les Arcs,
  France (1997).

\item The Status of the AMANDA High-Energy Neutrino Detector (with the
  AMANDA collaboration, S.W. Barwick \etal), {\it Proceedings of the
    25th International Cosmic Ray Conference}, Durban, South Africa,
  Vol.~7, 1 (1997).

\item THE AMANDA EXPERIMENT: status and prospects for indirect Dark
  Matter detection (with the AMANDA Collaboration, L.~Bergstr\"{o}m
  \etal), {\it Proceedings of the International Workshop on the
    Identification of Dark Matter (IDM 96)}, Sheffield, England, 1996,
  Edited by N.J.C. Spooner, p.521 (1997).


\item First Look at AMANDA-B Data (with the AMANDA collaboration,
  S. Tilav \etal), {\it Proceedings of the 25th International Cosmic
    Ray Conference}, Durban, South Africa, Vol.~7, 5 (1997).

\item Analysis of Cascades in AMANDA-A, (with the AMANDA
  collaboration, R. Porrata \etal), {\it Proceedings of the 25th
    International Cosmic Ray Conference}, Durban, South Africa,
  Vol.~7, 9 (1997).

\item Muon Reconstruction with AMANDA-B, (with the AMANDA
  collaboration, C.H. Wiebusch \etal), {\it Proceedings of the 25th
    International Cosmic Ray Conference}, Durban, South Africa,
  Vol.~7, 13 (1997).

\item Analysis of SPASE-AMANDA Coincidence Events (with the SPASE and
  AMANDA collaborations, T.C. Miller \etal), {\it Proceedings of the
    25th International Cosmic Ray Conference}, Durban, South Africa,
  Vol.~5, 237 (1997).

\item Status of the AMANDA and BAIKAL Neutrino Telescopes (with the
  AMANDA and BAIKAL Collaborations, P. Askebjer \etal), {\it Proc. 9th
    Intern. Symp. on Very High Energy Cosmic Ray Interactions},
  Karlsruhe, Germany, 1996, Edited by H. Rebel \etal, Nucl. Phys. B
  Suppl. 52B:256 (1997).

\item The AMANDA Neutrino Telescope And The Indirect Search For Dark
  Matter (with the AMANDA Collaboration, F. Halzen et
  al.). MADPH-98-1050 (Apr 1998). 16pp.  Talk given at 3rd
  International Symposium on Sources and Detection of Dark Matter in
  the Universe (DM 98), Santa Monica, CA (18-20 Feb 1998).  Published
  in Phys. Rept. {\bf 307} 243-252 (1998).  e-Print Archive:
  hep-ex/9804007.

\item An Overview Of Offline Software For AMANDA (with the AMANDA
  Collaboration, J. Jacobsen et al.). 1998.  Prepared for
  International Workshop on Simulations and Analysis Methods for Large
  Neutrino Telescopes, Zeuthen, Germany (6-9 Jul 1998). In Zeuthen
  1998, Simulation and Analysis Methods for Large Neutrino Telescopes
  194-204.

\item Initial Results From The AMANDA High-Energy Neutrino Detector
  (with the AMANDA Collaboration, S. W. Barwick et al.). 1998.
  Prepared for 29th International Conference on High-Energy Physics
  (ICHEP 98), Vancouver, British Columbia, Canada (23-29 Jul 1998). In
  Vancouver 1998, High Energy Physics, Vol. 2 1447-1452.

\item The AMANDA Neutrino Telescope (with the AMANDA Collaboration,
  Francis Halzen et al.). MADPH-98-1078 (Sep 1998). 12pp.  Talk given
  at 18th International Conference on Neutrino Physics and
  Astrophysics (NEUTRINO 98), Takayama, Japan (4-9 Jun 1998).
  Published in Nucl. Phys. Proc. Suppl. {\bf 77} 474-485 (1999). Also
  in Buxton 1998, The Identification of Dark Matter 501-507 e-Print
  Archive: hep-ex/9809025.

\item Up and Downgoing Muons in the AMANDA B4 Prototype Detector (with
  the AMANDA Collaboration, S. Hundertmark et al.), Proceedings of the
  XXVIth International Cosmic Ray Conference, Salt Lake City, Utah
  (1999).

\item Digital Optical Module \& System Design for a Km Scale Neutrino
  Detector in Ice (with the AMANDA Collaboration, D.M. Lowder et al.),
  Proceedings of the XXVIth International Cosmic Ray Conference, Salt
  Lake City, Utah (1999).

\item AMANDA Search for High Energy Neutrinos Accompanying Gamma Ray
  Bursts (with the AMANDA Collaboration, Ryan Bay et al.), Proceedings
  of the XXVIth International Cosmic Ray Conference, Salt Lake City,
  Utah (1999).

\item From the First Neutrino Telescope, the Antarctic Muon and
  Neutrino Detector Array AMANDA, to the IceCube Observatory (with the
  AMANDA Collaboration, F. Halzen et al.), Proceedings of the XXVIth
  International Cosmic Ray Conference, Salt Lake City, Utah (1999).

\item Optical Properties of South Pole Ice at Depths from 140 to 2300
  Meters (with the AMANDA Collaboration, Kurt Woschnagg et al.),
  Proceedings of the XXVIth International Cosmic Ray Conference, Salt
  Lake City, Utah (1999).

\item Search for Relativistic Monopoles with the AMANDA Detector (with
  the AMANDA Collaboration, Peter Niessen et al.), Proceedings of the
  XXVIth International Cosmic Ray Conference, Salt Lake City, Utah
  (1999).

\item Observation of Atmospheric Neutrino Events with AMANDA (with the
  AMANDA Collaboration, A. Karle et al.), Proceedings of the XXVIth
  International Cosmic Ray Conference, Salt Lake City, Utah (1999).

\item The AMANDA B 10 String Array (with the AMANDA Collaboration,
  Gary C. Hill et al.), Proceedings of the XXVIth International Cosmic
  Ray Conference, Salt Lake City, Utah (1999).

\item A Search for Point Sources of High Energy Neutrinos with the
  AMANDA Neutrino Telescope (with the AMANDA Collaboration, J.H. Kim
  et al.), Proceedings of the XXVIth International Cosmic Ray
  Conference, Salt Lake City, Utah (1999).

\item Status of the RICE Experiment (with the AMANDA Collaboration,
  G.M. Frichter et al.), Proceedings of the XXVIth International
  Cosmic Ray Conference, Salt Lake City, Utah (1999).

\item Seasonal Variation of the Muon Flux seen by AMANDA (with the
  AMANDA Collaboration, A. Bouchta et al.), Proceedings of the XXVIth
  International Cosmic Ray Conference, Salt Lake City, Utah (1999).

\item Supernova Burst Analysis with the Amanda Neutrino Telescope
  (with the AMANDA Collaboration, R. Wischnewski et al.), Proceedings
  of the XXVIth International Cosmic Ray Conference, Salt Lake City,
  Utah (1999).

\item Calibration of AMANDA with Coincident Events from SPASE 2 (with
  the AMANDA Collaboration, T.C. Miller et al.), Proceedings of the
  XXVIth International Cosmic Ray Conference, Salt Lake City, Utah
  (1999).

\item Nearly Vertical Upgoing Muons in the AMANDA B10 Detector (with
  the AMANDA Collaboration, Eva Dalberg et al.), Proceedings of the
  XXVIth International Cosmic Ray Conference, Salt Lake City, Utah
  (1999).

\item Digital Optical Module And System Design For A Km-Scale Neutrino
  Detector In Ice (with D. M. Lowder et al.), Proceedings of the
  XXVIth International Cosmic Ray Conference, Salt Lake City, Vol. 2,
  452-455 (1999).

\item From The First Neutrino Telescope, The Antarctic Muon And
  Neutrino Detector Array Amanda, To The IceCube Observatory (with
  F. Halzen et al.), Proceedings of the XXVIth International Cosmic
  Ray Conference, Salt Lake City, Vol. 2, 428-431 (1999).

\item The AMANDA Neutrino Detector (with the AMANDA Collaboration,
  R. Wischnewski et al.) (1999). Given at 10th International Symposium
  on Very High-Energy Cosmic Ray Interactions (ISVHECRI 98), Assergi,
  Italy (12-17 Jul 1998).  Published in Nucl. Phys. Proc. Suppl. {\bf
    75A} 412-414 (1999).

\item Observation Of Atmospheric Neutrino Events With The AMANDA
  Experiment. (with the AMANDA Collaboration, E. Andres et al.) (Jan
  1999). 5pp.  Talk given at 17th International Workshop on Weak
  Interactions and Neutrinos (WIN 99), Cape Town, South Africa (24-30
  Jan 1999). In Cape Town 1999, Weak Interactions and Neutrinos
  258-262.  e-Print Archive: astro-ph/9904379.

\item AMANDA: Status, Results and Future (with the AMANDA
  Collaboration, E. Andres et al.).  Talk given at 8th International
  Workshop on Neutrino Telescopes, Venice, Italy (23-26 Feb 1999).  In
  Venice 1999, Neutrino Telescopes, Vol. 2 63-79.

\item Status Of The AMANDA Experiment (with the AMANDA Collaboration,
  E. Andres et al.). 1999. Given at 5th International Workshop on
  Topics in Astroparticle and Underground Physics (TAUP 97), Gran
  Sasso, Italy (7-11 Sep 1997).  Published in
  Nucl. Phys. Proc. Suppl. {\bf 70} 448-452 (1999).

\item From AMANDA To IceCube: Current And Future High Energy Neutrino
  Telescopes At The South Pole (with the AMANDA Collaboration,
  T. Miller et al.). Jun 1999. Prepared for 23rd Johns Hopkins
  Workshop on Current Problems in Particle Theory: Neutrinos in the
  New Millennium, Baltimore, Maryland (10-12 Jun 1999).  Published in
  Baltimore 1999, Neutrinos in the New Millennium 47-61.

\item Wimp Searches With Amanda-B10 (with the AMANDA Collaboration,
  X. Bai et al.) (Sep 2000). 7pp. Contribution to the proceedings of
  3rd International Workshop on the Identification of Dark Matter
  (IDM2000), York, England (18-22 Sep 2000).  Published in York 2000,
  The Identification of Dark Matter 499-505. e-Print Archive:
  astro-ph/0012285.

\item Results From The AMANDA High-Energy Neutrino Detector (with the
  AMANDA Collaboration, E. Andres et al.) (Jun 2000). 8pp. Submitted
  to Int. Conf. Neut. Phys. Astro. (Neutrino 2000).  Published in
  Nucl. Phys. Proc. Suppl. {\bf 91} 423-430 (2000). Also in Sudbury
  2000, Neutrino Physics and Astrophysics 423-430. e-Print Archive:
  astro-ph/0009242.

\item The AMANDA Neutrino Detector: Status Report (with the AMANDA
  Collaboration, R. Wischnewski et al.) (2000).  Prepared for 6th
  Topical Seminar on Neutrino and AstroParticle Physics, San Miniato,
  Italy (17-21 May 1999).  Published in Nucl. Phys. Proc. Suppl. {\bf
    85} 141-145 (2000).

\item Status Of The Neutrino Telescope AMANDA: Monopoles And Wimps
  (with the AMANDA Collaboration, X. Bai et al.) (Jul 2000).  Prepared
  for 3rd International Conference on Dark Matter in Astro and
  Particle Physics (Dark 2000), Heidelberg, Germany (10-16 Jul 2000).
  Published in Heidelberg 2000, Dark Matter in Astro- and Particle
  Physics 699-706.

\item Selected Recent Results From AMANDA (with the AMANDA
  Collaboration, E. Andres et al.) (Jul 2000).  Prepared for 30th
  International Conference on High-Energy Physics (ICHEP 2000), Osaka,
  Japan (27 Jul - 2 Aug 2000).  Published in Osaka 2000, High Energy
  Physics, Vol. 2 965-968.

\item Calibration and Survey of AMANDA with SPASE (with the AMANDA
  Collaboration, X. Bai et al.), Proceedings of the XXVIIth
  International Cosmic Ray Conference, Hamburg, Germany (2001).

\item Time Calibration of the AMANDA Neutrino Telescope with Cosmic
  Ray Muons (with the AMANDA Collaboration, D. Cowen et al.),
  Proceedings of the XXVIIth International Cosmic Ray Conference,
  Hamburg, Germany (2001).

\item Analysis of Atmospheric Muons with AMANDA (with the AMANDA
  Collaboration, P. Desiati et al.), Proceedings of the XXVIIth
  International Cosmic Ray Conference, Hamburg, Germany (2001).

\item Supernova Neutrino-Burst Search with the AMANDA detector (with
  the AMANDA Collaboration, T. Neunhoeffer et al.), Proceedings of the
  XXVIIth International Cosmic Ray Conference, Hamburg, Germany
  (2001).

\item Search for Relativistic Monopoles with the AMANDA Detector (with
  the AMANDA Collaboration, P. Niessen et al.), Proceedings of the
  XXVIIth International Cosmic Ray Conference, Hamburg, Germany
  (2001).

\item Search for Cascade-like events in the AMANDA-B10 Detector (with
  the AMANDA Collaboration, I. Taboada et al.), Proceedings of the
  XXVIIth International Cosmic Ray Conference, Hamburg, Germany
  (2001).

\item The AMANDA Search for High Energy Neutrinos from Gamma Ray
  Bursts (with the AMANDA Collaboration, R. Hardtke et al.),
  Proceedings of the XXVIIth International Cosmic Ray Conference,
  Hamburg, Germany (2001).

\item A Method to Detect UHE Neutrinos with AMANDA (with the AMANDA
  Collaboration, S. Hundertmark et al.), Proceedings of the XXVIIth
  International Cosmic Ray Conference, Hamburg, Germany (2001).

\item Search for a Diffuse Flux from Sources of High Energy Neutrinos
  with AMANDA B-10 (with the AMANDA Collaboration G. Hill et al.),
  Proceedings of the XXVIIth International Cosmic Ray Conference,
  Hamburg, Germany (2001).

\item Observation of High Energy Atmospheric Neutrinos with AMANDA
  (with the AMANDA Collaboration, C. Wiebusch et al.), Proceedings of
  the XXVIIth International Cosmic Ray Conference, Hamburg, Germany
  (2001).

\item Performance of the AMANDA-II Detector (with the AMANDA
  Collaboration, M. Kowalski et al.), Proceedings of the XXVIIth
  International Cosmic Ray Conference, Hamburg, Germany (2001).

\item Potential of AMANDA-II in HE Neutrino Astrophysics (with the
  AMANDA Collaboration, S. Barwick et al.), Proceedings of the XXVIIth
  International Cosmic Ray Conference, Hamburg, Germany (2001).

\item Observation of High-energy Neutrinos Using Cerenkov Detectors
  Embedded Deep in Antarctic Ice (with the AMANDA Collaboration),
  Proceedings of the XXVIIth International Cosmic Ray Conference,
  Hamburg, Germany (2001).

\item Muon Monte Carlo: A New High-precision Tool for Muon Propagation
  Through Matter (with the AMANDA Collaboration, D. Chirkin et al.),
  Proceedings of the XXVIIth International Cosmic Ray Conference,
  Hamburg, Germany (2001).

\item Recent Results From AMANDA (with the AMANDA Collaboration,
  E. Andres et al.).  Prepared for DPF 2000: The Meeting of the
  Division of Particles and Fields of the American Physical Society,
  Columbus, Ohio (9-12 Aug 2000).  Published in
  Int. J. Mod. Phys. {\bf A16S1C} 1013-1015 (2001).

\item Physics Results From The AMANDA Neutrino Detector (with the
  AMANDA Collaboration, Marek Kowalski et al.) (Dec 2001). 5pp.  To
  appear in the proceedings of International Europhysics Conference on
  High-Energy Physics (HEP 2001), Budapest, Hungary (12-18 Jul 2001).
  Published in Budapest 2001, High Energy Physics hep2001/207 e-Print
  Archive: hep-ph/0112083.

\item Results From AMANDA (with the AMANDA Collaboration, J. Ahrens et
  al.) (Mar 2001).  Prepared for 9th International Symposium on
  Neutrino Telescopes, Venice, Italy (6-9 Mar 2001).  Published in
  Venice 2001, Neutrino Telescopes, Vol. 2 569-580.

\item Initial Results from AMANDA (with the AMANDA Collaboration,
  J. Ahrens et al.).  Prepared for 21st Rencontres de Moriond Workshop
  on Very High-Energy Phenomena in the Universe, Les Arcs, France
  (20-27 Jan 2001).  Published in Les Arcs 2001, Very High Energy
  Phenomena in the Universe NAP-T4.

\item Observation of High Energy Atmospheric Neutrinos with AMANDA
  (with the AMANDA Collaboration, A. Karle et al.).  Prepared for 7th
  Conference on Intersections Between Particle and Nuclear Physics
  (CIPANP 2000), Quebec City, Quebec, Canada (22-28 May 2000).  AIP
  Conf. Proc. {\bf 549} 823-827 (2002).

\item Recent Results from AMANDA II (with the AMANDA Collaboration,
  K. Hanson et al.).  Prepared for 31st International Conference on
  High Energy Physics (ICHEP 2002), Amsterdam, The Netherlands (24-31
  Jul 2002). Published in Amsterdam 2002, ICHEP 126-128.

\item Physics and Operation of the AMANDA-II High Energy Neutrino
  Telescope (with the AMANDA Collaboration, J. Ahrens et al.).  To
  appear in the proceedings of Conference on Astronomical Telescopes
  and Instrumenation, Waikoloa, Hawaii (22-28 Aug 2002).

\item IceCube - the Next Generation Neutrino Telescope at the South
  Pole (with the IceCube Collaboration, A. Karle et al.).  8pp.
  e-Print archive: arXiv:astro-ph/0209556v1 (2002).

\item IceCube - The Next Generation Neutrino Telescope at the South
  Pole (with the IceCube Collaboration, J. Ahrens et al.).  To appear
  in the proceedings of 20th International Conference on Neutrino
  Physics and Astrophysics (Neutrino 2002), Munich, Germany (25-30 May
  2002).  Nucl. Phys. Proc. Suppl. {\bf 118} 388-395 (2003).

\item Results from the Antarctic Muon and Neutrino Detector Array
  (AMANDA) (with the AMANDA Collaboration, J. Ahrens et al.).
  Nucl. Phys. Proc. Suppl. {\bf 118} 371-379 (2003).
~
\item The IceCube Project (with the IceCube Collaboration, Christian
  Spiering et al.).  Talk given at VLVnT Workshop on Technical Aspects
  of a Very Large Volume Neutrino Telescope in the Mediterrenean Sea,
  Amsterdam, The Netherlands (5-8 Oct 2003). Published in Amsterdam
  2003, Technical aspects of a Very Large Volume Neutrino Telescope in
  the Mediterranean Sea 21-25.

\item Results from the AMANDA Telescope. (with the AMANDA
  Collaboration, J. Ahrens et al.).  Nucl. Phys. {\bf A721} 545-548
  (2003).

\item Recent Results from the AMANDA Experiment (with the AMANDA
  Collaboration, Peter Niessen et al.).  To appear in the proceedings
  of 38th Rencontres de Moriond on Electroweak Interactions and
  Unified Theories, Les Arcs, France (15-22 Mar 2003.)

\item Results from the AMANDA Neutrino Gelescope (C. de los Heros et
  al..  Prepared for CRIS 2004: 5th Cosmic Ray International Seminar:
  GZK and Surroundings, Catania, Italy (31 May - 4 Jun 2004).
  Published in Nucl. Phys. Proc. Suppl. {\bf 136} 85-92 (2004). Also
  in Catania 2004, GZK and Surroundings 85-92.

\item Results from the AMANDA Detector (with the AMANDA Collaboration,
  P. Olbrechts et al.).  Prepared for Cracow Epiphany Conference on
  Astroparticle Physics, Cracow, Poland (8-11 Jan 2004).  Published in
  Acta Phys. Polon. {\bf B35} 1919-1931 (2004).

\item Status of the IceCube Neutrino Observatory (with the IceCube
  Collaboration, J. Ahrens et al.).  Prepared for 2nd VERITAS
  Symposium on TeV Astrophysics of Extragalactic Sources, Chicago,
  Illinois (24-26 Apr 2003).  Published in New Astron. Rev. {\bf 48}
  519-525 (2004).

\item New Results from the Antarctic Muon and Neutrino Detector Array
  (with the AMANDA Collaboration, J. Ahrens et al.).  To appear in the
  proceedings of 21st International Conference on Neutrino Physics and
  Astrophysics (Neutrino 2004), Paris, France (14-19 Jun
  2004). Published in Nucl. Phys. Proc. Suppl. {\bf 143} 343-350
  (2005). Also in Paris 2004, Neutrino Physics and Astrophysics
  343-350.

\item IceCube: The Cubic Kilometer Neutrino Telescope at the South
  Pole (with the IceCube Collaboration, A.R. Fazely et al.).  8pp.
  e-Print archive: astro-ph/0406125v1 (2004).

\item Multi-messenger Studies with AMANDA/IceCube: Observations and
  Strategies (with IceCube Collaboration, A. Achterberg et al.).  To
  appear in the proceedings of 7th Workshop on Towards a Network of
  Atmospheric Cherenkov Detectors 2005, Palaiseau, France (27-29 Apr
  2005).

\item Results from the AMANDA Neutrino Telescope (with the AMANDA
  Collaboration, J. Ahrens et al.).  Nucl. Phys. Proc. Suppl. {\bf
    138} 167-170 (2005).

\item The IceCube Collaboration: Contributions to the 29th
  International Cosmic Ray Conference (ICRC 2005), Pune, India,
  Aug. 2005 (with the IceCube Collaboration, A. Achterberg et al.).
  Contributed to 29th International Cosmic Ray Conference (ICRC 2005),
  Pune, India (3-11 Aug 2005).

\item From AMANDA to IceCube (with the IceCube collaboration, Mathieu
  Ribordy et al.).  Phys. Atom. Nucl. {\bf 69} 1899-1907 (2006).

\item IceCube - Construction Status, Performance Results of the 22
  String Detector (with the IceCube Collaboration, A. Karle et al.),
  Proceedings of the XXXth International Cosmic Ray Conference,
  Merida, Mexico (2007).

\item The Combined AMANDA and IceCube Neutrino Telescope (with the
  IceCube Collaboration, A. Gross et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item Performance of the IceTop Array (with the IceCube Collaboration,
  T.K. Gaisser et al.), Proceedings of the XXXth International Cosmic
  Ray Conference, Merida, Mexico (2007).

\item Heliospheric Physics with IceTop (with the IceCube
  Collaboration, T. Kubawara et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item Measuring Cosmic Ray Composition at the Knee with SPASE-2 and
  AMANDA (with the IceCube and SPASE-2 Collaborations, K.G. Andeen et
  al.), Proceedings of the XXXth International Cosmic Ray Conference,
  Merida, Mexico (2007).

\item Cosmic Rays in IceCube: Composition-sensitive Observables (with
  the IceCube Collaboration, C. Song et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item Search for TeV gamma-rays from Point Sources with SPASE-2 (with
  the IceCube and SPASE-2 Collaborations, K. James et al.),
  Proceedings of the XXXth International Cosmic Ray Conference,
  Merida, Mexico (2007).

\item Study of High Pt Muons in Air Showers with IceCube (with the
  IceCube Collaboration, S. Klein et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item IceTop/IceCube Coincidences (with the IceCube Collaboration,
  X. Bai et al.), Proceedings of the XXXth International Cosmic Ray
  Conference, Merida, Mexico (2007).

\item Lateral Distribution of Air Shower Signals and Initial Energy
  Spectrum Above 1 PeV from IceTop (with the IceCube Collaboration,
  S. Klepser et al.), Proceedings of the XXXth International Cosmic
  Ray Conference, Merida, Mexico (2007).

\item IceTop Tank Response to Muons (with the IceCube Collaboration,
  L. Demirors et al.), Proceedings of the XXXth International Cosmic
  Ray Conference, Merida, Mexico (2007).

\item Response of IceTop Tanks to Low-energy Particles (with the
  IceCube Collaboration, J.M. Clem et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item Testing Alternative Oscillation Scenarios with Atmospheric
  Neutrinos Using AMANDA-II Data (with the IceCube Collaboration,
  J. Ahrens et al.), Proceedings of the XXXth International Cosmic Ray
  Conference, Merida, Mexico (2007).

\item Atmospheric Muon Neutrino Analysis with IceCube (with the
  IceCube Collaboration, J. Pretz et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item Muon Energy Reconstruction and Atmospheric Neutrino Spectrum
  Unfolding with the IceCube Detector (with the IceCube Collaboration,
  J.D. Zornoza et al.), Proceedings of the XXXth International Cosmic
  Ray Conference, Merida, Mexico (2007).

\item Searches for a Diffuse Flux of Extra-terrestrial Muon Neutrinos
  with AMANDA-II and IceCube (with the IceCube Collaboration,
  K. Hoshina et al.), Proceedings of the XXXth International Cosmic
  Ray Conference, Merida, Mexico (2007).

\item Measurement of the Atmospheric Lepton Energy Spectra with
  AMANDA-II (with the IceCube Collaboration, K. Munich et al.),
  Proceedings of the XXXth International Cosmic Ray Conference,
  Merida, Mexico (2007).

\item Multi-year Search for UHE Diffuse Neutrino Flux with AMANDA-II
  (with the IceCube Collaboration, L. Gerhardt), Proceedings of the
  XXXth International Cosmic Ray Conference, Merida, Mexico (2007).

\item Likelihood Deconvolution of Diffuse Prompt and Extra-terrestrial
  Neutrino Fluxes in the AMANDA-II Detector (with the IceCube
  Collaboration, G.C. Hill et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item Search for Neutrino-induced Cascades with AMANDA Data Taken in
  2000-2004 (O. Tarasova et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item EHE Neutrino Search with the IceCube 9 String Array (with the
  IceCube Collaboration, A. Ishihara et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item Very High Energy Electromagnetic Cascades in the LPM Regime with
  IceCube (with the IceCube Collaboration, J. Bolmont et al.),
  Proceedings of the XXXth International Cosmic Ray Conference,
  Merida, Mexico (2007).

\item IceCube Performance with Artificial Light Sources: The Road to
  Cascade Analyses (with the IceCube Collaboration, J. Kiryluk et
  al.), Proceedings of the XXXth International Cosmic Ray Conference,
  Merida, Mexico (2007).

\item Neutrino Point Source Search Strategies for AMANDA-II and
  Results from 2005 (with the IceCube Collaboration, J. Braun et al.),
  Proceedings of the XXXth International Cosmic Ray Conference,
  Merida, Mexico (2007).

\item Point Source Analysis for Cosmic Neutrinos Beyond PeV Energies
  with AMANDA and IceCube (with the IceCube Collaboration, R. Franke
  et al.), Proceedings of the XXXth International Cosmic Ray
  Conference, Merida, Mexico (2007).

\item Nine-string IceCube Point Source Analysis (with the IceCube
  Collaboration, C. Finley et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item Search for Signatures of Extra-terrestrial Neutrinos with a
  Multipole Analysis of the AMANDA-II Sky-map (with the IceCube
  Collaboration, J.P. Hulss et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item Cluster Search for Neutrino Flares from Pre-defined Directions
  (with the IceCube Collaboration, K. Satalecka et al.), Proceedings
  of the XXXth International Cosmic Ray Conference, Merida, Mexico
  (2007).

\item All-sky Search for Transient Sources of Neutrinos Using Give
  Years of AMANDA-II Data (with the IceCube Collaboration, R. Porrata
  et al.), Proceedings of the XXXth International Cosmic Ray
  Conference, Merida, Mexico (2007).

\item Neutrino Triggered Target of Opportunity (NToO) Test Run with
  AMANDA-II and MAGIC (with the IceCube and MAGIC Collaborations,
  M. Ackerman et al.), Proceedings of the XXXth International Cosmic
  Ray Conference, Merida, Mexico (2007).

\item Detecting GRBs with IceCube and Optical Follow-up Observations
  (with the IceCube Collaboration, A. Kappes et al.), Proceedings of
  the XXXth International Cosmic Ray Conference, Merida, Mexico
  (2007).

\item Search for Neutralino Dark Matter with the AMANDA Neutrino
  Telescope (with the IceCube Collaboration, D. Hubert et al.),
  Proceedings of the XXXth International Cosmic Ray Conference,
  Merida, Mexico (2007).

\item Prospects of Dark Matter Detection in IceCube (with the IceCube
  Collaboration, G. Wikstrom et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item Search for Relativistic Magnetic Monopoles with the AMANDA-II
  Detector (with the IceCube Collaboration, H. Wissing et al.),
  Proceedings of the XXXth International Cosmic Ray Conference,
  Merida, Mexico (2007).

\item Subrelativistic Particle Searches with the AMANDA-II Detector
  (with the IceCube Collaboration, A. Pohl et al.), Proceedings of the
  XXXth International Cosmic Ray Conference, Merida, Mexico (2007).

\item Exotic Particles Searches with IceCube (with the IceCube
  Collaboration, B. Christy et al.), Proceedings of the XXXth
  International Cosmic Ray Conference, Merida, Mexico (2007).

\item Effect of the Improved Data Acquisition System of IceCube on its
  Neutrino-detection Capabilities (with the IceCube Collaboration,
  D. Chirkin et al.), Proceedings of the XXXth International Cosmic
  Ray Conference, Merida, Mexico (2007).

\item Improved Cherenkov Light Propagation Methods for the IceCube
  Neutrino Telescope (with the IceCube Collaboration, J. Lundberg et
  al.), Proceedings of the XXXth International Cosmic Ray Conference,
  Merida, Mexico (2007).

\item Reconstruction of High Energy Muon Events in IceCube Using
  Waveforms (with the IceCube Collaboration, S. Grullon et al.),
  Proceedings of the XXXth International Cosmic Ray Conference,
  Merida, Mexico (2007).

\item Radio Detection of GZK Neutrinos - AURA Status and Plans (with
  the IceCube Collaboration, H. Landsman et al.), Proceedings of the
  XXXth International Cosmic Ray Conference, Merida, Mexico (2007).


\end{enumerate}

{\bf New Stuff:}\footnote{To File}
\vspace{0.25cm}

\begin{enumerate}

\bibitem{:2012uib} 
  M. G. Aartsen {\it et al.}  [IceCube Collaboration],
  ``Search for Galactic PeV Gamma Rays with the IceCube Neutrino Observatory,'' Oct. 2012.
  arXiv:1210.7992 [astro-ph.HE].
  %%CITATION = ARXIV:1210.7992;%%

\bibitem{Aartsen:2012ma} 
  M.~G.~Aartsen, R.~Abbasi, Y.~Abdou, M.~Ackermann, J.~Adams, J.~A.~Aguilar, M.~Ahlers and D.~Altmann {\it et al.},
  ``Observation of Cosmic Ray Anisotropy with the IceTop Air Shower Array,'' Oct. 2012.
  arXiv:1210.5278 [astro-ph.HE].
  %%CITATION = ARXIV:1210.5278;%%

\bibitem{Abbasi:2012ws} 
  R.~Abbasi {\it et al.}  [IceCube Collaboration],
  ``Search for Neutrinos from Annihilating Dark Matter in the Direction of the Galactic Center with the 40-String IceCube Neutrino Observatory,'' Oct. 2012.
  arXiv:1210.3557 [hep-ex].
  %%CITATION = ARXIV:1210.3557;%%

\bibitem{IceCube:2012sj} 
  R.~Abbasi {\it et al.}  [IceCube Collaboration],
  ``Searches for high-energy neutrino emission in the Galaxy with the combined IceCube-AMANDA detector,'' Oct. 2012.
  arXiv:1210.3273 [astro-ph.HE].
  %%CITATION = ARXIV:1210.3273;%%

\bibitem{:2012rh} 
  R.~Abbasi {\it et al.}  [IceCube Collaboration],
  ``Search for Relativistic Magnetic Monopoles with IceCube,'' Aug. 2012.
  arXiv:1208.4861 [astro-ph.HE].
  %%CITATION = ARXIV:1208.4861;%%

\bibitem{:2012re} 
  R.~Abbasi {\it et al.}  [IceCube Collaboration],
  ``An improved method for measuring muon energy using the truncated mean of dE/dx,'' Aug. 2012.
  arXiv:1208.3430 [physics.data-an].
  %%CITATION = ARXIV:1208.3430;%%

\bibitem{:2012ij} 
  R.~Abbasi {\it et al.}  [IceCube Collaboration],
  ``Lateral Distribution of Muons in IceCube Cosmic Ray Events,'' Aug. 2012.
  arXiv:1208.2979 [astro-ph.HE].
  %%CITATION = ARXIV:1208.2979;%%

\bibitem{IceCube:2012nn} 
  R.~Abbasi {\it et al.}  [IceCube Collaboration],
  ``IceTop: The surface component of IceCube,'' Jul. 2012.
  arXiv:1207.6326 [astro-ph.IM].
  %%CITATION = ARXIV:1207.6326;%%

\bibitem{IceCube:2012vv} 
  R.~Abbasi {\it et al.}  [IceCube Collaboration],
  ``Cosmic Ray Composition and Energy Spectrum from 1-30 PeV Using the 40-String Configuration of IceTop and IceCube,'' Jul. 2012.
  arXiv:1207.3455 [astro-ph.HE].
  %%CITATION = ARXIV:1207.3455;%%

\end{enumerate}

{\bf Even MORE stuff}

\begin{enumerate}

%{:2012uib}
\item ``Search for Galactic PeV Gamma Rays with the IceCube Neutrino
  Observatory'' (with the IceCube Collaboration). arXiv:1210.7992 [astro-ph.HE]
 
%(Oct 2012)
%\href{http://inspirehep.net/record/1194082}{HEP entry}


%{Aartsen:2012ma}
\item ``Observation of Cosmic Ray Anisotropy with the IceTop Air Shower
  Array'' (with M.~G.~Aartsen, R.~Abbasi, Y.~Abdou, M.~Ackermann,
  J.~Adams, J.~A.~Aguilar, M.~Ahlers and D.~Altmann {\it et al.}).
  arXiv:1210.5278 [astro-ph.HE]
  
 %(Oct 2012)
%\href{http://inspirehep.net/record/1191836}{HEP entry}


%{Abbasi:2012ws}
\item ``Search for Neutrinos from Annihilating Dark Matter in the Direction
  of the Galactic Center with the 40-String IceCube Neutrino
  Observatory'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1210.3557 [hep-ex]
  
 %(Oct 2012)
%\href{http://inspirehep.net/record/1190495}{HEP entry}


%{IceCube:2012sj}
\item ``Searches for high-energy neutrino emission in the Galaxy with the
  combined IceCube-AMANDA detector'' (with R.~Abbasi {\it et al.}
  [IceCube Collaboration]). arXiv:1210.3273 [astro-ph.HE]
  
 %(Oct 2012)
%\href{http://inspirehep.net/record/1190336}{HEP entry}

%{:2012rh}
\item ``Search for Relativistic Magnetic Monopoles with IceCube'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1208.4861 [astro-ph.HE]
  
 %(Aug 2012)
%\href{http://inspirehep.net/record/1181730}{HEP entry}


%{:2012re}
\item ``An improved method for measuring muon energy using the truncated
  mean of dE/dx'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1208.3430 [physics.data-an]
  
 %(Aug 2012)
%\href{http://inspirehep.net/record/1127702}{HEP entry}


%{:2012ij}
\item ``Lateral Distribution of Muons in IceCube Cosmic Ray Events'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1208.2979 [astro-ph.HE]
  
 %(Aug 2012)
%\href{http://inspirehep.net/record/1127552}{HEP entry}


%{IceCube:2012nn}
\item ``IceTop: The surface component of IceCube'' (with R.~Abbasi {\it et
  al.}  [IceCube Collaboration]).  \\{}arXiv:1207.6326 [astro-ph.IM]
  
 %(Jul 2012)
%\href{http://inspirehep.net/record/1123894}{HEP entry}


%{IceCube:2012vv}
\item ``Cosmic Ray Composition and Energy Spectrum from 1-30 PeV Using the
  40-String Configuration of IceTop and IceCube'' (with R.~Abbasi {\it
    et al.}  [IceCube Collaboration]).  \\{}arXiv:1207.3455
  [astro-ph.HE]
  
 %(Jul 2012)
%\href{http://inspirehep.net/record/1122617}{HEP entry}


%{Scott:2012mq}
\item ``Use of event-level neutrino telescope data in global fits for
  theories of new physics'' (with P.~Scott {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:1207.0810 [hep-ph]
  
 %(Jul 2012)
%\href{http://inspirehep.net/record/1121068}{HEP entry}


%{Abbasi:2012zw}
\item ``An absence of neutrinos associated with cosmic-ray acceleration in
  $\gamma$-ray bursts'' (with R.~Abbasi {\it et al.}  [IceCube
  Collaboration]).  \\{}arXiv:1204.4219 [astro-ph.HE]
  \\{}10.1038/nature11068 \\{}Nature {\bf 484}, 351 (2012) %(Apr 2012)
%\href{http://inspirehep.net/record/1111580}{HEP entry}


%{Abbasi:2012cu}
\item ``A Search for UHE Tau Neutrinos with IceCube'' (with R.~Abbasi {\it et
  al.}  [IceCube Collaboration]).  \\{}arXiv:1202.4564 [astro-ph.HE]
  \\{}10.1103/PhysRevD.86.022005 \\{}Phys.\ Rev.\ D {\bf 86}, 022005
  (2012) %(Feb 2012)
%\href{http://inspirehep.net/record/1089833}{HEP entry}


%{Abbasi:2012wn}
\item ``All-particle cosmic ray energy spectrum measured with 26 IceTop
  stations'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1202.3039 [astro-ph.HE]
  
 %(Feb 2012)
%\href{http://inspirehep.net/record/1089093}{HEP entry}


%{IceCube:2011aj}
\item ``Multi-year search for dark matter annihilations in the Sun with the
  AMANDA-II and IceCube detectors'' (with R.~Abbasi {\it et al.}
  [IceCube Collaboration]).  \\{}arXiv:1112.1840 [astro-ph.HE]
  \\{}10.1103/PhysRevD.85.042002 \\{}Phys.\ Rev.\ D {\bf 85}, 042002
  (2012) %(Dec 2011)
%\href{http://inspirehep.net/record/1080491}{HEP entry}


%{Abbasi:2011ja}
\item ``Searching for soft relativistic jets in Core-collapse Supernovae
  with the IceCube Optical Follow-up Program'' (with R.~Abbasi {\it et
    al.}  [IceCube and ROTSE Collaborations].  \\{}arXiv:1111.7030
  [astro-ph.HE] \\{}Astron.\ Astrophys.\ {\bf 539}, A60 (2012) %(Nov
  2011)
%\href{http://inspirehep.net/record/1079525}{HEP entry}


%{IceCube:2011ab}
\item ``IceCube - Astrophysics and Astroparticle Physics at the South Pole'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1111.5188 [astro-ph.HE]
  
 %(Nov 2011)
%\href{http://inspirehep.net/record/947009}{HEP entry}


%{Abbasi:2011zx}
\item ``Studies on the unfolding of the atmospheric neutrino spectrum with
  IceCube 59 using the TRUEE algorithm'' (with R.~Abbasi {\it et al.}
  [IceCube Collaboration]).  \\{}arXiv:1111.2736 [astro-ph.HE]
  
 %(Aug 2011)
%\href{http://inspirehep.net/record/945596}{HEP entry}


%{IceCube:2011ae}
\item ``The IceCube Neutrino Observatory IV: Searches for Dark Matter and
  Exotic Particles'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:1111.2738 [astro-ph.HE]
  
 %(Nov 2011)
%\href{http://inspirehep.net/record/945595}{HEP entry}


%{IceCube:2011ad}
\item ``The IceCube Neutrino Observatory I: Point Source Searches'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1111.2741 [astro-ph.HE]
  
 %(Nov 2011)
%\href{http://inspirehep.net/record/945594}{HEP entry}


%{IceCube:2011ac}
\item ``The IceCube Neutrino Observatory V: Future Developments'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1111.2742 [astro-ph.IM]
  
 %(Nov 2011)
%\href{http://inspirehep.net/record/945593}{HEP entry}


%{Collaboration:2011ym}
\item ``The Design and Performance of IceCube DeepCore'' (with R.~Abbasi {\it
  et al.}  [IceCube Collaboration]).  \\{}arXiv:1109.6096 [astro-ph.IM]
  \\{}10.1016/j.astropartphys.2012.01.004 \\{}Astropart.\ Phys.\ {\bf
    35}, 615 (2012) %(Sep 2011)
%\href{http://inspirehep.net/record/929836}{HEP entry}


%{Abbasi:2011zka}
\item ``Observation of an Anisotropy in the Galactic Cosmic Ray arrival
  direction at 400 TeV with IceCube'' (with R.~Abbasi {\it et al.}
  [IceCube Collaboration]).  \\{}arXiv:1109.1017 [hep-ex]
  \\{}10.1088/0004-637X/746/1/33 \\{}Astrophys.\ J.\ {\bf 746}, 33
  (2012) %(Sep 2011)
%\href{http://inspirehep.net/record/926572}{HEP entry}


%{Abbasi:2011ke}
\item ``Searches for periodic neutrino emission from binary systems with 22
  and 40 strings of IceCube'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:1108.3023 [astro-ph.HE]
  \\{}10.1088/0004-637X/748/2/118 \\{}Astrophys.\ J.\ {\bf 748}, 118
  (2012) %(Aug 2011)
%\href{http://inspirehep.net/record/924073}{HEP entry}



%{Abbasi:2011ss}
\item ``IceCube Sensitivity for Low-Energy Neutrinos from Nearby
  Supernovae'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1108.0171 [astro-ph.HE] \\{}Astron.\ Astrophys.\ {\bf
    535}, A109 (2011) %(Aug 2011)
%\href{http://inspirehep.net/record/921747}{HEP entry}


%{IceCube:2011aa}
\item ``Neutrino analysis of the September 2010 Crab Nebula flare and
  time-integrated constraints on neutrino emission from the Crab using
  IceCube'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1106.3484 [astro-ph.HE] \\{}10.1088/0004-637X/745/1/45
  \\{}Astrophys.\ J.\ {\bf 745}, 45 (2012) %(Jun 2011)
%\href{http://inspirehep.net/record/914129}{HEP entry}


%{Abbasi:2011ai}
\item ``Observation of Anisotropy in the Arrival Directions of Galactic
  Cosmic Rays at Multiple Angular Scales with IceCube'' (with R.~Abbasi
  {\it et al.}  [IceCube Collaboration]).  \\{}arXiv:1105.2326
  [astro-ph.HE] \\{}10.1088/0004-637X/740/1/16
  \\{}Astrophys.\ J.\ {\bf 740}, 16 (2011) %(May 2011)
%\href{http://inspirehep.net/record/899347}{HEP entry}


%{Abbasi:2011jx}
\item ``A Search for a Diffuse Flux of Astrophysical Muon Neutrinos with the
  IceCube 40-String Detector'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:1104.5187 [astro-ph.HE]
  \\{}10.1103/PhysRevD.84.082001 \\{}Phys.\ Rev.\ D {\bf 84}, 082001
  (2011) %(Apr 2011)
%\href{http://inspirehep.net/record/897343}{HEP entry}


%{IceCube:2011ai}
\item ``Time-Dependent Searches for Point Sources of Neutrinos with the
  40-String and 22-String Configurations of IceCube'' (with R.~Abbasi
  {\it et al.}  [IceCube Collaboration]).  \\{}arXiv:1104.0075
  [astro-ph.HE] \\{}10.1088/0004-637X/744/1/1 \\{}Astrophys.\ J.\ {\bf
    744}, 1 (2012) %(Apr 2011)
%\href{http://inspirehep.net/record/894722}{HEP entry}


%{Abbasi:2011ji}
\item ``Constraints on the Extremely-high Energy Cosmic Neutrino Flux with
  the IceCube 2008-2009 Data'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:1103.4250 [astro-ph.CO]
  \\{}10.1103/PhysRevD.84.079902, 10.1103/PhysRevD.83.092003
  \\{}Phys.\ Rev.\ D {\bf 83}, 092003 (2011), [Erratum-ibid.\ D {\bf
      84}, 079902 (2011)] %(Mar 2011)
%\href{http://inspirehep.net/record/893525}{HEP entry}


%{Abbasi:2011zy}
\item ``Background studies for acoustic neutrino detection at the South
  Pole'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1103.1216 [astro-ph.IM]
  \\{}10.1016/j.astropartphys.2011.09.004 \\{}Astropart.\ Phys.\ {\bf
    35}, 312 (2012) %(Mar 2011)
%\href{http://inspirehep.net/record/891585}{HEP entry}



%{Abbasi:2011wh}
\item ``Constraints on high-energy neutrino emission from SN 2008D'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1101.3942 [astro-ph.HE] \\{}Astron.\ Astrophys.\ {\bf
    527}, A28 (2011) %(Jan 2011)
%\href{http://inspirehep.net/record/884841}{HEP entry}


%{Abbasi:2011zzy}
\item ``Search for neutrino-induced cascades with five years of AMANDA
  data'' (with R.~Abbasi, Y.~Abdou, T.~Abu-Zayyad, O.~Actis, J.~Adams,
  J.~A.~Aguilar, M.~Ahlers and K.~Andeen {\it et al.}). 10.1016/j.astropartphys.2010.10.007 \\{}Astropart.\ Phys.\ {\bf
    34}, 420 (2011). %(2011)
%\href{http://inspirehep.net/record/884627}{HEP entry}


%{Abbasi:2011eq}
\item ``Search for Dark Matter from the Galactic Halo with the IceCube
  Neutrino Observatory'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:1101.3349 [astro-ph.HE]
  \\{}10.1103/PhysRevD.84.022004 \\{}Phys.\ Rev.\ D {\bf 84}, 022004
  (2011) %(Jan 2011)
%\href{http://inspirehep.net/record/884587}{HEP entry}


%{Abbasi:2011ui}
\item ``First search for atmospheric and extraterrestrial neutrino-induced
  cascades with the IceCube detector'' (with R.~Abbasi {\it et al.}
  [IceCube Collaboration]).  \\{}arXiv:1101.1692 [astro-ph.HE]
  \\{}10.1103/PhysRevD.84.072001 \\{}Phys.\ Rev.\ D {\bf 84}, 072001
  (2011) %(Jan 2011)
%\href{http://inspirehep.net/record/883987}{HEP entry}


%{Abbasi:2011qc}
\item ``Limits on Neutrino Emission from Gamma-Ray Bursts with the 40 String
  IceCube Detector'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:1101.1448 [astro-ph.HE]
  \\{}10.1103/PhysRevLett.106.141101 \\{}Phys.\ Rev.\ Lett.\ {\bf
    106}, 141101 (2011) %(Jan 2011)
%\href{http://inspirehep.net/record/883689}{HEP entry}


%{Abbasi:2010rd}
\item ``Time-Integrated Searches for Point-like Sources of Neutrinos with
  the 40-String IceCube Detector'' (with R.~Abbasi {\it et al.}
  [IceCube Collaboration]).  \\{}arXiv:1012.2137 [astro-ph.HE]
  \\{}10.1088/0004-637X/732/1/18 \\{}Astrophys.\ J.\ {\bf 732}, 18
  (2011) %(Dec 2010)
%\href{http://inspirehep.net/record/880956}{HEP entry}


%{Abbasi:2010kx}
\item ``Search for a Lorentz-violating sidereal signal with atmospheric
  neutrinos in IceCube'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:1010.4096 [astro-ph.HE]
  \\{}10.1103/PhysRevD.82.112003 \\{}Phys.\ Rev.\ D {\bf 82}, 112003
  (2010) %(Oct 2010)
%\href{http://inspirehep.net/record/873535}{HEP entry}


%{Abbasi:2010ie}
\item ``Measurement of the atmospheric neutrino energy spectrum from 100 GeV
  to 400 TeV with IceCube'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:1010.3980 [astro-ph.HE]
  \\{}10.1103/PhysRevD.83.012001 \\{}Phys.\ Rev.\ D {\bf 83}, 012001
  (2011) %(Oct 2010)
%\href{http://inspirehep.net/record/873313}{HEP entry}

%{Ofek:2010kq}
\item ``Supernova PTF 09uj: A possible shock breakout from a dense
  circumstellar wind'' (with E.~O.~Ofek, I.~Rabinak, J.~D.~Neill,
  I.~Arcavi, S.~B.~Cenko, E.~Waxman, S.~R.~Kulkarni and A.~G.~Yam {\it
    et al.}.  \\{}arXiv:1009.5378 [astro-ph.HE]
  \\{}10.1088/0004-637X/724/2/1396 \\{}Astrophys.\ J.\ {\bf 724}, 1396
  (2010) %(Sep 2010)
%\href{http://inspirehep.net/record/871153}{HEP entry}


%{Abbasi:2010ak}
\item ``The first search for extremely-high energy cosmogenic neutrinos with
  the IceCube Neutrino Observatory'' (with R.~Abbasi {\it et al.}
  [IceCube Collaboration]).  \\{}arXiv:1009.1442 [astro-ph.CO]
  \\{}10.1103/PhysRevD.82.072003 \\{}Phys.\ Rev.\ D {\bf 82}, 072003
  (2010) %(Sep 2010)
%\href{http://inspirehep.net/record/868041}{HEP entry}


%{Abbasi:2010zz}
\item ``Search for relativistic magnetic monopoles with the AMANDA-II
  neutrino telescope'' (with R.~Abbasi, Y.~Abdou, T.~Abu-Zayyad,
  J.~Adams, J.~A.~Aguilar, M.~Ahlers, K.~Andeen and J.~Auffenberg {\it
    et al.}.  \\{}10.1140/epjc/s10052-010-1411-6
  \\{}Eur.\ Phys.\ J.\ C {\bf 69}, 361 (2010). %(Aug 28, 2010)
%\href{http://inspirehep.net/record/867712}{HEP entry}


%{Abbasi:2010mf}
\item ``Measurement of the Anisotropy of Cosmic Ray Arrival Directions with
  IceCube'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1005.2960 [astro-ph.HE] \\{}10.1088/2041-8205/718/2/L194
  \\{}Astrophys.\ J.\ {\bf 718}, L194 (2010) %(May 2010)
%\href{http://inspirehep.net/record/855469}{HEP entry}


%{Rawlins:2008zz}
\item ``IceCube: A multipurpose neutrino telescope'' (with K.~Rawlins {\it et
  al.}  [IceCube Collaboration]). J.\ Phys.\ Soc.\ Jap.\ Suppl.\ {\bf 77B}, 71 (2008). %(2008)
%\href{http://inspirehep.net/record/854669}{HEP entry}


%{Abbasi:2010qv}
\item ``The Energy Spectrum of Atmospheric Neutrinos between 2 and 200 TeV
  with the AMANDA-II Detector'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:1004.2357 [astro-ph.HE]
  \\{}10.1016/j.astropartphys.2010.05.001 \\{}Astropart.\ Phys.\ {\bf
    34}, 48 (2010) %(Apr 2010)
%\href{http://inspirehep.net/record/851947}{HEP entry}


%{Abbasi:2010ki}
\item ``IceCube Collaboration Contributions to the 2009 International Cosmic
  Ray Conference'' (with R.~Abbasi, Y.~Abdou, T.~Abu-Zayyad, J.~Adams,
  J.~A.~Aguilar, M.~Ahlers, K.~Andeen and J.~Auffenberg {\it et al.}). arXiv:1004.2093 [astro-ph.HE]
  
 %(Apr 2010)
%\href{http://inspirehep.net/record/851735}{HEP entry}


%{Abbasi:2010vt}
\item ``Measurement of Acoustic Attenuation in South Pole Ice'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1004.1694 [astro-ph.IM]
  \\{}10.1016/j.astropartphys.2010.10.003 \\{}Astropart.\ Phys.\ {\bf
    34}, 382 (2011) %(Apr 2010)
%\href{http://inspirehep.net/record/851565}{HEP entry}


%{Arcavi:2010wd}
\item ``Core-Collapse Supernovae from the Palomar Transient Factory:
  Indications for a Different Population in Dwarf Galaxies'' (with I.~Arcavi, A.~Gal-Yam, M.~M.~Kasliwal, R.~M.~Quimby, E.~O.~Ofek,
  S.~R.~Kulkarni, P.~E.~Nugent and S.~B.~Cenko {\it et al.}). arXiv:1004.0615 [astro-ph.CO] \\{}10.1088/0004-637X/721/1/777
  \\{}Astrophys.\ J.\ {\bf 721}, 777 (2010) %(Apr 2010)
%\href{http://inspirehep.net/record/850861}{HEP entry}


%{Abbasi:2010vc}
\item ``Calibration and Characterization of the IceCube Photomultiplier
  Tube'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:1002.2442 [astro-ph.IM] \\{}10.1016/j.nima.2010.03.102
  \\{}Nucl.\ Instrum.\ Meth.\ A {\bf 618}, 139 (2010) %(Feb 2010)
%\href{http://inspirehep.net/record/845761}{HEP entry}


%{Abbasi:2009cv}
\item ``Extending the search for neutrino point sources with IceCube above
  the horizon'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:0911.2338 [astro-ph.HE] \\{}10.1103/PhysRevLett.103.221102
  \\{}Phys.\ Rev.\ Lett.\ {\bf 103}, 221102 (2009) %(Nov 2009)
%\href{http://inspirehep.net/record/836741}{HEP entry}


%{Abbasi:2009vg}
\item ``Limits on a muon flux from Kaluza-Klein dark matter annihilations in
  the Sun from the IceCube 22-string detector'' (with R.~Abbasi {\it et
    al.}  [IceCube Collaboration]).  \\{}arXiv:0910.4480 [astro-ph.CO]
  \\{}10.1103/PhysRevD.81.057101 \\{}Phys.\ Rev.\ D {\bf 81}, 057101
  (2010) %(Oct 2009)
%\href{http://inspirehep.net/record/834994}{HEP entry}


%{Abbasi:2009si}
\item ``Measurement of sound speed vs. depth in South Pole ice for neutrino
  astronomy'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:0909.2629 [astro-ph.IM]
  \\{}10.1016/j.astropartphys.2010.01.012 \\{}Astropart.\ Phys.\ {\bf
    33}, 277 (2010) %(Sep 2009)
%\href{http://inspirehep.net/record/831166}{HEP entry}


%{Abbasi:2009ig}
\item ``Search for muon neutrinos from Gamma-Ray Bursts with the IceCube
  neutrino telescope'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:0907.2227 [astro-ph.HE]
  \\{}10.1088/0004-637X/710/1/346 \\{}Astrophys.\ J.\ {\bf 710}, 346
  (2010) %(Jul 2009)
%\href{http://inspirehep.net/record/825578}{HEP entry}


%{Law:2009ys}
\item ``The Palomar Transient Factory: System Overview, Performance and
  First Results'' (with N.~M.~Law, S.~R.~Kulkarni, R.~G.~Dekany,
  E.~O.~Ofek, R.~M.~Quimby, P.~E.~Nugent, J.~Surace and
  C.~C.~Grillmair {\it et al.}.  \\{}arXiv:0906.5350 [astro-ph.IM]
  
 %(Jun 2009)
%\href{http://inspirehep.net/record/824366}{HEP entry}


%{Abbasi:2009iv}
\item ``First Neutrino Point-Source Results From the 22-String IceCube
  Detector'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:0905.2253 [astro-ph.HE] \\{}10.1088/0004-637X/701/1/L47
  \\{}Astrophys.\ J.\ {\bf 701}, L47 (2009) %(May 2009)
%\href{http://inspirehep.net/record/820454}{HEP entry}



%{Abbasi:2009uz}
\item ``Limits on a muon flux from neutralino annihilations in the Sun with
  the IceCube 22-string detector'' (with R.~Abbasi {\it et al.}
  [ICECUBE Collaboration]).  \\{}arXiv:0902.2460 [astro-ph.CO]
  \\{}10.1103/PhysRevLett.102.201302 \\{}Phys.\ Rev.\ Lett.\ {\bf
    102}, 201302 (2009) %(Feb 2009)
%\href{http://inspirehep.net/record/813331}{HEP entry}


%{Abbasi:2009nfa}
\item ``Determination of the Atmospheric Neutrino Flux and Searches for New
  Physics with AMANDA-II'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:0902.0675 [astro-ph.HE]
  \\{}10.1103/PhysRevD.79.102005 \\{}Phys.\ Rev.\ D {\bf 79}, 102005
  (2009) %(Feb 2009)
%\href{http://inspirehep.net/record/812524}{HEP entry}


%{Abbasi:2009kq}
\item ``Search for high-energy muon neutrinos from the 'naked-eye' GRB
  080319B with the IceCube neutrino telescope'' (with R.~Abbasi {\it et
    al.}  [IceCube Collaboration]).  \\{}arXiv:0902.0131 [astro-ph.HE]
  \\{}10.1088/0004-637X/701/2/1721, 10.1088/0004-637X/708/1/911
  \\{}Astrophys.\ J.\ {\bf 701}, 1721 (2009), [Erratum-ibid.\ {\bf
      708}, 911 (2010)] %(Feb 2009)
%\href{http://inspirehep.net/record/812295}{HEP entry}


%{Abbasi:2008aa}
\item ``The IceCube Data Acquisition System: Signal Capture, Digitization,
  and Timestamping'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:0810.4930 [physics.ins-det]
  \\{}10.1016/j.nima.2009.01.001 \\{}Nucl.\ Instrum.\ Meth.\ A {\bf
    601}, 294 (2009) %(Oct 2008)
%\href{http://inspirehep.net/record/800773}{HEP entry}


%{Abbasi:2008vr}
\item ``Solar Energetic Particle Spectrum on 13 December 2006 Determined by
  IceTop'' (with R.~Abbasi {\it et al.}  [IceCube Collaboration]). arXiv:0810.2034 [astro-ph]
  
 %(Oct 2008)
%\href{http://inspirehep.net/record/799149}{HEP entry}


%{Abbasi:2008ih}
\item ``Search for Point Sources of High Energy Neutrinos with Final Data
  from AMANDA-II'' (with R.~Abbasi {\it et al.}  [IceCube
    Collaboration]).  \\{}arXiv:0809.1646 [astro-ph]
  \\{}10.1103/PhysRevD.79.062001 \\{}Phys.\ Rev.\ D {\bf 79}, 062001
  (2009) %(Sep 2008)
%\href{http://inspirehep.net/record/796085}{HEP entry}


%{Ackermann:2007km}
\item ``Search for Ultra High-Energy Neutrinos with AMANDA-II'' (with M.~Ackermann {\it et al.}  [IceCube Collaboration]). arXiv:0711.3022 [astro-ph] \\{}10.1086/527046
  \\{}Astrophys.\ J.\ {\bf 675}, 1014 (2008) %(Nov 2007)
%\href{http://inspirehep.net/record/768127}{HEP entry}


%{Achterberg:2007bi}
\item ``Detection of Atmospheric Muon Neutrinos with the IceCube 9-String
  Detector'' (with A.~Achterberg {\it et al.}  [IceCube Collaboration]). arXiv:0705.1781 [astro-ph] \\{}10.1103/PhysRevD.76.027101
  \\{}Phys.\ Rev.\ D {\bf 76}, 027101 (2007) %(May 2007)
%\href{http://inspirehep.net/record/750455}{HEP entry}


%{Achterberg:2007qp}
\item ``Multi-year search for a diffuse flux of muon neutrinos with
  AMANDA-II'' (with A.~Achterberg {\it et al.}  [IceCube Collaboration]). arXiv:0705.1315 [astro-ph] \\{}10.1103/PhysRevD.76.042008,
  10.1103/PhysRevD.77.089904 \\{}Phys.\ Rev.\ D {\bf 76}, 042008
  (2007), [Erratum-ibid.\ D {\bf 77}, 089904 (2008)] %(May 2007)
%\href{http://inspirehep.net/record/750251}{HEP entry}


%{Achterberg:2007nx}
\item ``The Search for Muon Neutrinos from Northern Hemisphere Gamma-Ray
  Bursts with AMANDA'' (with A.~Achterberg {\it et al.}  [IceCube and
    IPN Collaborations].  \\{}arXiv:0705.1186 [astro-ph]
  \\{}10.1086/524920 \\{}Astrophys.\ J.\ {\bf 674}, 357 (2008) %(May
  2007)
%\href{http://inspirehep.net/record/750212}{HEP entry}


%{Achterberg:2007qy}
\item ``Search for neutrino-induced cascades from gamma-ray bursts with
  AMANDA'' (with A.~Achterberg {\it et al.}  [IceCube Collaboration]). astro-ph/0702265 \\{}10.1086/518596 \\{}Astrophys.\ J.\ {\bf
    664}, 397 (2007) %(Mar 2007)
%\href{http://inspirehep.net/record/744243}{HEP entry}


%{Achterberg:2006pw}
\item ``Contributions to 2nd TeV Particle Astrophysics Conference (TeV PA
  II). Madison, Wisconsin 28-31 Aug 2006'' (with A.~Achterberg {\it et
    al.}  [IceCube Collaboration]).  \\{}astro-ph/0611597
  \\{}%Submitted to: J.Phys.Conf.Ser. %(Nov 2006)
%\href{http://inspirehep.net/record/732188}{HEP entry}


%{Achterberg:2006jf}
\item ``Limits on the muon flux from neutralino annihilations at the center
  of the Earth with AMANDA'' (with A.~Achterberg {\it et al.}  [AMANDA
    Collaboration]).  \\{}10.1016/j.astropartphys.2006.05.007
  \\{}Astropart.\ Phys.\ {\bf 26}, 129 (2006). %(2006)
%\href{http://inspirehep.net/record/732124}{HEP entry}


%{Achterberg:2006vc}
\item ``Five years of searches for point sources of astrophysical neutrinos
  with the AMANDA-II neutrino telescope'' (with A.~Achterberg {\it et
    al.}  [IceCube Collaboration]).  \\{}astro-ph/0611063
  \\{}10.1103/PhysRevD.75.102001 \\{}Phys.\ Rev.\ D {\bf 75}, 102001
  (2007) %(Nov 2006)
%\href{http://inspirehep.net/record/730687}{HEP entry}


%{Achterberg:2006ik}
\item ``On the selection of AGN neutrino source candidates for a source
  stacking analysis with neutrino telescopes'' (with A.~Achterberg {\it
    et al.}  [IceCube Collaboration]).  \\{}astro-ph/0609534
  \\{}10.1016/J.ASTROPARTPHYS.2006.06.012 \\{}Astropart.\ Phys.\ {\bf
    26}, 282 (2006) %(Sep 2006)
%\href{http://inspirehep.net/record/726462}{HEP entry}


%{Achterberg:2006az}
\item ``Limits on the high-energy gamma and neutrino fluxes from the SGR
  1806-20 giant flare of December 27th, 2004 with the AMANDA-II
  detector'' (with A.~Achterberg {\it et al.}  [IceCube Collaboration]). astro-ph/0607233 \\{}10.1103/PhysRevLett.97.221101
  \\{}Phys.\ Rev.\ Lett.\ {\bf 97}, 221101 (2006) %(Jul 2006)
%\href{http://inspirehep.net/record/721227}{HEP entry}


%{Achterberg:2006md}
\item ``First Year Performance of The IceCube Neutrino Telescope'' (with A.~Achterberg {\it et al.}  [IceCube Collaboration]). astro-ph/0604450 \\{}10.1016/j.astropartphys.2006.06.007
  \\{}Astropart.\ Phys.\ {\bf 26}, 155 (2006) %(Apr 2006)
%\href{http://inspirehep.net/record/715057}{HEP entry}


%{Ackermann:2006gp}
\item ``The ICECUBE prototype string in AMANDA'' (with M.~Ackermann {\it et
  al.}  [AMANDA Collaboration]).  \\{}astro-ph/0601397
  \\{}10.1016/j.nima.2005.10.029 \\{}Nucl.\ Instrum.\ Meth.\ A {\bf
    556}, 169 (2006) %(Jan 2006)
%\href{http://inspirehep.net/record/708768}{HEP entry}


%{Desiati:2005hk}
\item ``Neutrino astronomy and cosmic rays at the South Pole: Latest results
  from AMANDA and perspectives for IceCube'' (with P.~Desiati {\it et
    al.}  [AMANDA and IceCube Collaboration]). 10.1142/S0217751X0503048X \\{}Int.\ J.\ Mod.\ Phys.\ A {\bf 20},
  6919 (2005). %(2005)
%\href{http://inspirehep.net/record/703122}{HEP entry}


%{Achterberg:2005mn}
\item ``Multi-messenger studies with amanda/icecube: observations and
  strategies'' (with A.~Achterberg {\it et al.}  [IceCube
    Collaboration]).  \\{}astro-ph/0509396
  
 %(Sep 2005)
%\href{http://inspirehep.net/record/692130}{HEP entry}


%{Achterberg:2005fs}
\item ``The icecube collaboration: contributions to the 29th international
  cosmic ray conference (icrc 2005), pune, india, aug. 2005'' (with A.~Achterberg {\it et al.}  [IceCube Collaboration]). astro-ph/0509330
  
 %(Sep 2005)
%\href{http://inspirehep.net/record/692009}{HEP entry}


%{Ribordy:2005fi}
\item ``From amanda to icecube'' (with M.~Ribordy {\it et al.}  [IceCube
  Collaboration]).  \\{}astro-ph/0509322 \\{}10.1134/S1063778806110147
  \\{}Phys.\ Atom.\ Nucl.\ {\bf 69}, 1899 (2006) %(Sep 2005)
%\href{http://inspirehep.net/record/692001}{HEP entry}


%{Ackermann:2005fr}
\item ``Limits to the muon flux from neutralino annihilations in the sun
  with the amanda detector'' (with M.~Ackermann {\it et al.}  [AMANDA
    Collaboration]).  \\{}astro-ph/0508518
  \\{}10.1016/j.astropartphys.2005.09.006 \\{}Astropart.\ Phys.\ {\bf
    24}, 459 (2006) %(Aug 2005)
%\href{http://inspirehep.net/record/690671}{HEP entry}


%{Ackermann:2005aa}
\item ``New results from the AMANDA neutrino telescope'' (with M.~Ackermann
  {\it et al.}  [AMANDA Collaboration]). 10.1016/j.nuclphysbps.2005.04.030
  \\{}Nucl.\ Phys.\ Proc.\ Suppl.\ {\bf 145}, 319 (2005). %(2005)
%\href{http://inspirehep.net/record/685676}{HEP entry}


%{Ackermann:2005sb}
\item ``Flux limits on ultra high energy neutrinos with AMANDA-B10'' (with M.~Ackermann, J.~Ahrens, H.~Albrecht, D.~Atlee, X.~Bai, R.~Bay,
  M.~Bartelt and S.~W.~Barwick {\it et al.}). 10.1016/j.astropartphys.2004.09.008 \\{}Astropart.\ Phys.\ {\bf
    22}, 339 (2005). %(2005)
%\href{http://inspirehep.net/record/675327}{HEP entry}


%{delosHeros:2004nk}
\item ``Results from the AMANDA neutrino telescope'' (with C.~de los Heros,
  M.~Ackermann, J.~Ahrens, H.~Albrecht, X.~Bai, R.~Bay, M.~Bartelt and
  S.~W.~Barwick {\it et al.}.  \\{}10.1016/j.nuclphysbps.2004.10.003
  \\{}Nucl.\ Phys.\ Proc.\ Suppl.\ {\bf 136}, 85 (2004). %(2004)
%\href{http://inspirehep.net/record/669763}{HEP entry}


%{Ackermann:2004aga}
\item ``Search for extraterrestrial point sources of high energy neutrinos
  with AMANDA-II using data collected in 2000-2002'' (with M.~Ackermann
  {\it et al.}  [AMANDA Collaboration]).  \\{}astro-ph/0412347
  \\{}10.1103/PhysRevD.71.077102 \\{}Phys.\ Rev.\ D {\bf 71}, 077102
  (2005) %(Dec 2004)
%\href{http://inspirehep.net/record/667006}{HEP entry}


%{Ahrens:2004nn}
\item ``Measurement of the cosmic ray composition at the knee with the
  SPASE-2/AMANDA-B10 detectors'' (with J.~Ahrens {\it et al.}  [AMANDA
    and SPASE Collaboration]).  \\{}10.1016/j.astropartphys.2004.04.007
  \\{}Astropart.\ Phys.\ {\bf 21}, 565 (2004). %(2004)
%\href{http://inspirehep.net/record/664098}{HEP entry}


%{Olbrechts:2004nb}
\item ``Results from the AMANDA detector'' (with P.~Olbrechts {\it et al.}
  [AMANDA Collaboration]).  \\{}Acta Phys.\ Polon.\ B {\bf 35}, 1919
  (2004). %(2004)
%\href{http://inspirehep.net/record/662608}{HEP entry}


%{Ahrens:2004qq}
\item ``New results from the Antarctic Muon and Neutrino Detector Array'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]). astro-ph/0409423 \\{}10.1016/j.nuclphysbps.2005.01.127
  \\{}Nucl.\ Phys.\ Proc.\ Suppl.\ {\bf 143}, 343 (2005) %(Sep 2004)
%\href{http://inspirehep.net/record/659561}{HEP entry}


%{Ahrens:2004dg}
\item ``Calibration and survey of AMANDA with the SPASE detectors'' (with J.~Ahrens {\it et al.}  [SPASE and AMANDA Collaboration]). 10.1016/j.nima.2003.12.007 \\{}Nucl.\ Instrum.\ Meth.\ A {\bf
    522}, 347 (2004). %(2004)
%\href{http://inspirehep.net/record/659314}{HEP entry}


%{Ahrens:2004ay}
\item ``Status of the IceCube Neutrino Observatory'' (with J.~Ahrens {\it et
  al.}  [IceCube Collaboration]).  \\{}10.1016/j.newar.2003.12.031
  \\{}New Astron.\ Rev.\ {\bf 48}, 519 (2004). %(2004)
%\href{http://inspirehep.net/record/651595}{HEP entry}


%{Ribordy:2004um}
\item ``AMANDA: Status and latest results'' (with M.~Ribordy {\it et al.}
  [AMANDA Collaboration]).  \\{}hep-ex/0405035
  
 %(May 2004)
%\href{http://inspirehep.net/record/650386}{HEP entry}


%{Ackermann:2004zw}
\item ``Search for neutrino-induced cascades with AMANDA'' (with M.~Ackermann
  {\it et al.}  [AMANDA Collaboration]).  \\{}astro-ph/0405218
  \\{}10.1016/j.astropartphys.2004.06.003 \\{}Astropart.\ Phys.\ {\bf
    22}, 127 (2004) %(May 2004)
%\href{http://inspirehep.net/record/650190}{HEP entry}


%{Spiering:2004dm}
\item ``The IceCube Project'' (with C.~Spiering {\it et al.}  [IceCube
  Collaboration]).  \\{}astro-ph/0404090
  
 %(Apr 2004)
%\href{http://inspirehep.net/record/647582}{HEP entry}


%{Ahrens:2003fg}
\item ``Muon track reconstruction and data selection techniques in AMANDA'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]). astro-ph/0407044 \\{}10.1016/j.nima.2004.01.065
  \\{}Nucl.\ Instrum.\ Meth.\ A {\bf 524}, 169 (2004) %(Sep 2003)
%\href{http://inspirehep.net/record/637644}{HEP entry}


%{Ahrens:2003qd}
\item ``Results from the AMANDA neutrino telescope'' (with J.~Ahrens {\it et
  al.}  [AMANDA Collaboration]).  \\{}10.1016/j.nuclphysbps.2004.11.039
  \\{}Nucl.\ Phys.\ Proc.\ Suppl.\ {\bf 138}, 167 (2005). %(Mar 2003)
%\href{http://inspirehep.net/record/634595}{HEP entry}


%{Ahrens:2003kw}
\item ``Results from the AMANDA telescope'' (with J.~Ahrens {\it et al.}
  [AMANDA Collaboration]).  \\{}10.1016/S0375-9474(03)01120-5
  \\{}Nucl.\ Phys.\ A {\bf 721}, 545 (2003). %(2003)
%\href{http://inspirehep.net/record/631985}{HEP entry}


%{Ahrens:2003pv}
\item ``Search for extraterrestrial point sources of neutrinos with
  AMANDA-II'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]). astro-ph/0309585 \\{}10.1103/PhysRevLett.92.071102
  \\{}Phys.\ Rev.\ Lett.\ {\bf 92}, 071102 (2004) %(Sep 2003)
%\href{http://inspirehep.net/record/628728}{HEP entry}


%{Niessen:2003xi}
\item ``Recent results from the amanda experiment'' (with P.~Niessen {\it et
  al.}  [AMANDA Collaboration]).  \\{}astro-ph/0306209
  
 %(Jun 2003)
%\href{http://inspirehep.net/record/620706}{HEP entry}


%{Ahrens:2003ix}
\item ``Sensitivity of the IceCube detector to astrophysical sources of high
  energy muon neutrinos'' (with J.~Ahrens {\it et al.}  [IceCube
    Collaboration]).  \\{}astro-ph/0305196
  \\{}10.1016/j.astropartphys.2003.09.003 \\{}Astropart.\ Phys.\ {\bf
    20}, 507 (2004) %(May 2003)
%\href{http://inspirehep.net/record/618572}{HEP entry}


%{Ahrens:2003ee}
\item ``Limits on diffuse fluxes of high-energy extraterrestrial neutrinos
  with the AMANDA-B10 detector'' (with J.~Ahrens, X.~Bai, S.~W.~Barwick,
  R.~C.~Bay, T.~Becka, K.~-H.~Becker, E.~Bernardini and D.~Bertrand
  {\it et al.}.  \\{}astro-ph/0303218
  \\{}10.1103/PhysRevLett.90.251101 \\{}Phys.\ Rev.\ Lett.\ {\bf 90},
  251101 (2003) %(Mar 2003)
%\href{http://inspirehep.net/record/614855}{HEP entry}


%{Hanson:2002ye}
\item ``Recent results from AMANDA II'' (with K.~Hanson {\it et al.}  [AMANDA
  Collaboration]).
  
 %(Jul 2002)
%\href{http://inspirehep.net/record/608388}{HEP entry}


%{Karle:2002zh}
\item ``Observation of high energy atmospheric neutrinos with AMANDA'' (with A.~Karle {\it et al.}  [AMANDA Collaboration]). 10.1063/1.1345374 \\{}AIP Conf.\ Proc.\ {\bf 549}, 823
  (2000). %(2000)
%\href{http://inspirehep.net/record/604945}{HEP entry}


%{Wiebusch:2002ij}
\item ``Results from AMANDA'' (with C.~Wiebusch {\it et al.}  [AMANDA
  Collaboration]).  \\{}10.1142/S0217732302008575
  \\{}Mod.\ Phys.\ Lett.\ A {\bf 17}, 2019 (2002). %(2002)
%\href{http://inspirehep.net/record/603512}{HEP entry}


%{Ahrens:2002du}
\item ``Physics and operation of the AMANDA-II High Energy Neutrino
  Telescope'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]). astro-ph/0211269
  
 %(Nov 2002)
%\href{http://inspirehep.net/record/601887}{HEP entry}


%{Ahrens:2002vb}
\item ``Results from the Antarctic Muon and Neutrino Detector Array (AMANDA)'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]). astro-ph/0211264
    \\{}10.1016/S0920-5632(03)01335-5
\\{}Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 118}, 371 (2003) %(Nov 2002)
%\href{http://inspirehep.net/record/601819}{HEP entry}


%{Ahrens:2002dv}
\item ``Icecube - the next generation neutrino telescope at the south pole'' (with J.~Ahrens {\it et al.}  [IceCube Collaboration]). astro-ph/0209556
\\{}Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 118}, 388 (2003) %(Sep 2002)
%\href{http://inspirehep.net/record/597012}{HEP entry}


%{Ahrens:2002hh}
\item ``Search for point sources of high energy neutrinos with AMANDA'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]). astro-ph/0208006
    \\{}10.1086/345352
\\{}Astrophys.\ J.\  {\bf 583}, 1040 (2003) %(Aug 2002)
%\href{http://inspirehep.net/record/591714}{HEP entry}


%{Ahrens:2002wz}
\item ``Search for neutrino-induced cascades with the AMANDA detector'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]). astro-ph/0206487
    \\{}10.1103/PhysRevD.67.012003
\\{}Phys.\ Rev.\ D {\bf 67}, 012003 (2003) %(Jun 2002)
%\href{http://inspirehep.net/record/589398}{HEP entry}


%{Ahrens:2002gq}
\item ``Observation of high-energy atmospheric neutrinos with the Antarctic Muon and Neutrino Detector Array'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]). astro-ph/0205109
    \\{}10.1103/PhysRevD.66.012005
\\{}Phys.\ Rev.\ D {\bf 66}, 012005 (2002) %(May 2002)
%\href{http://inspirehep.net/record/586602}{HEP entry}



%{Ahrens:2002eb}
\item ``Limits to the muon flux from WIMP annihilation in the center of the Earth with the AMANDA detector'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]). astro-ph/0202370
    \\{}10.1103/PhysRevD.66.032006
\\{}Phys.\ Rev.\ D {\bf 66}, 032006 (2002) %(Feb 2002)
%\href{http://inspirehep.net/record/583168}{HEP entry}


%{Ahrens:2001mk}
\item ``Initial results from AMANDA'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]).
  
 %(Jan 2001)
%\href{http://inspirehep.net/record/579929}{HEP entry}


%{Andres:2001fc}
\item ``Recent results from AMANDA'' (with E.~Andres {\it et al.}  [AMANDA Collaboration]). Int.\ J.\ Mod.\ Phys.\ A {\bf 16S1C}, 1013 (2001). %(2001)
%\href{http://inspirehep.net/record/571320}{HEP entry}


%{Kowalski:2001th}
\item ``Physics results from the AMANDA neutrino detector'' (with M.~Kowalski {\it et al.}  [AMANDA Collaboration]). hep-ph/0112083
  
 %(Dec 2001)
%\href{http://inspirehep.net/record/567816}{HEP entry}


%{Ahrens:2001wb}
\item ``Results from AMANDA'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]).
  
 %(Mar 2001)
%\href{http://inspirehep.net/record/565821}{HEP entry}



%{Ahrens:2001tz}
\item ``Search for supernova neutrino bursts with the AMANDA detector'' (with J.~Ahrens {\it et al.}  [AMANDA Collaboration]). astro-ph/0105460
    \\{}10.1016/S0927-6505(01)00154-2
\\{}Astropart.\ Phys.\  {\bf 16}, 345 (2002) %(May 2001)
%\href{http://inspirehep.net/record/557168}{HEP entry}


%{Andres:2001ty}
\item ``Observation of high-energy neutrinos using Cherenkov detectors embedded deep in Antarctic ice'' (with E.~Andres, P.~Askebjer, X.~Bai, G.~Barouch, S.~W.~Barwick, R.~C.~Bay, K.~H.~Becker and L.~Bergstrom {\it et al.}). 10.1038/35068509
\\{}Nature {\bf 410}, 441 (2001). %(Mar 2001)
%\href{http://inspirehep.net/record/555147}{HEP entry}



%{Andres:2000zf}
\item ``Selected recent results from AMANDA'' (with E.~Andres {\it et al.}  [AMANDA Collaboration]).
  
 %(Jul 2000)
%\href{http://inspirehep.net/record/543383}{HEP entry}


%{Bai:2000bk}
\item ``Status of the neutrino telescope AMANDA: Monopoles and WIMPs'' (with X.~Bai {\it et al.}  [AMANDA Collaboration]).
  
 %(Jul 2000)
%\href{http://inspirehep.net/record/542492}{HEP entry}



%{Bai:2000mb}
\item ``WIMP searches with AMANDA-B10'' (with X.~Bai {\it et al.}  [AMANDA Collaboration]). astro-ph/0012285
  
 %(Sep 2000)
%\href{http://inspirehep.net/record/538636}{HEP entry}


%{Andres:2000jf}
\item ``Results from the AMANDA high-energy neutrino detector'' (with E.~Andres {\it et al.}  [AMANDA Collaboration]). astro-ph/0009242
    \\{}10.1016/S0920-5632(00)00971-3
\\{}Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 91}, 423 (2001) %(Jun 2000)
%\href{http://inspirehep.net/record/533773}{HEP entry}


%{Wischnewski:2000ys}
\item ``The AMANDA neutrino detector: Status report'' (with R.~Wischnewski {\it et al.}  [AMANDA Collaboration]). 10.1016/S0920-5632(00)00497-7
\\{}Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 85}, 141 (2000). %(2000)
%\href{http://inspirehep.net/record/530642}{HEP entry}


%{Miller:1999ua}
\item ``From AMANDA to IceCube: Current and future high energy neutrino telescopes at the South Pole'' (with T.~Miller {\it et al.}  [AMANDA Collaboration]).
  
 %(Jun 1999)
%\href{http://inspirehep.net/record/516658}{HEP entry}


%{Wischnewski:1999yt}
\item ``The AMANDA Neutrino Detector'' (with R.~Wischnewski, E.~Andres, P.~Askebjer, S.~Barwick, R.~Bay, L.~Bergstrom, A.~Biron and J.~Booth {\it et al.}). Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 75A}, 412 (1999). %(1999)
%\href{http://inspirehep.net/record/505534}{HEP entry}


%{Lowder:1999kj}
\item ``Digital optical module and system design for a km-scale neutrino detector in ice'' (with D.~M.~Lowder, K.~H.~Becker, D.~Cowen, C.~Guenther, V.~Drozdov, A.~Karle and H.~Leich {\it et al.}). 10.1016/S1387-6473(98)00016-5
\\{}New Astron.\ Rev.\  {\bf 42}, 301 (1998). %(May 1999)
%\href{http://inspirehep.net/record/503668}{HEP entry}


%{Halzen:1999jy}
\item ``From the first neutrino telescope, the antarctic muon and neutrino detector array AMANDA, to the IceCube observatory'' (with F.~Halzen {\it et al.}  [AMANDA Collaboration]). In *Salt Lake City 1999, Cosmic ray, vol. 2* 428-431 %(May 1999)
%\href{http://inspirehep.net/record/503657}{HEP entry}


%{Andres:1999hp}
\item ``AMANDA: Status, results and future'' (with E.~Andres {\it et al.}  [AMANDA Collaboration]). astro-ph/9906205
  \\{}In *Venice 1999, Neutrino telescopes, vol. 2* 63-79 %(Feb 1999)
%\href{http://inspirehep.net/record/501602}{HEP entry}


%{Andres:1999hm}
\item ``The AMANDA neutrino telescope: Principle of operation and first results'' (with E.~Andres, P.~Askebjer, S.~W.~Barwick, R.~Bay, L.~Bergstrom, A.~Biron, J.~Booth and A.~Bouchta {\it et al.}). astro-ph/9906203, astro-ph/9906203
    \\{}10.1016/S0927-6505(99)00092-4
\\{}Astropart.\ Phys.\  {\bf 13}, 1 (2000) %(Jun 1999)
%\href{http://inspirehep.net/record/501600}{HEP entry}


%{Andres:1999yh}
\item ``Observation of atmospheric neutrino events with the AMANDA experiment'' (with E.~Andres {\it et al.}  [AMANDA Collaboration]). astro-ph/9904379
  \\{}In *Cape Town 1999, Weak interactions and neutrinos* 258-262 %(Jan 1999)
%\href{http://inspirehep.net/record/498938}{HEP entry}


%{Andres:1999bf}
\item ``Status of the AMANDA experiment'' (with E.~Andres {\it et al.}  [AMANDA Collaboration]). 10.1016/S0920-5632(98)00468-X
\\{}Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 70}, 448 (1999). %(1999)
%\href{http://inspirehep.net/record/493565}{HEP entry}


%{Jacobsen:1998vr}
\item ``An overview of offline software for AMANDA'' (with C.~Wiebusch {\it et al.} [AMANDA Collaboration]). In *Zeuthen 1998, Simulation and analysis methods for large neutrino telescopes* 194-204 %(1998)
%\href{http://inspirehep.net/record/486128}{HEP entry}


%{Barwick:1998re}
\item ``Initial results from the AMANDA high-energy neutrino detector'' (with S.~W.~Barwick, J.~Booth, J.~Kim, R.~Mock, R.~Porrata, D.~Ross, W.~Wu and G.~Yodh {\it et al.}). In *Vancouver 1998, High energy physics, vol. 2* 1447-1452 %(1998)
%\href{http://inspirehep.net/record/485628}{HEP entry}


%{Halzen:1998bp}
\item ``The AMANDA neutrino telescope'' (with F.~Halzen {\it et al.}  [AMANDA Collaboration]). hep-ex/9809025
    \\{}10.1016/S0920-5632(99)00469-7
\\{}Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 77}, 474 (1999) %(Sep 1998)
%\href{http://inspirehep.net/record/476721}{HEP entry}


%{Halzen:1998sc}
\item ``The AMANDA neutrino telescope and the indirect search for dark matter'' (with F.~Halzen {\it et al.}  [AMANDA Collaboration]). hep-ex/9804007
    \\{}10.1016/S0370-1573(98)00041-6
\\{}Phys.\ Rept.\  {\bf 307}, 243 (1998) %(Apr 1998)
%\href{http://inspirehep.net/record/469305}{HEP entry}


%{Askebjer:1997ep}
\item ``Optical properties of deep ice at the South Pole: Absorption'' (with P.~Askebjer, S.~W.~Barwick, L.~Bergstrom, A.~Bouchta, S.~Carius, E.~Dalberg, K.~Engel and B.~Erlandsson {\it et al.}). physics/9701025
\\{}Appl.\ Opt.\  {\bf 36}, 4168 (1997) %(Jun 1997)
%\href{http://inspirehep.net/record/458400}{HEP entry}


%{Wiebusch:1997vd}
\item ``Status of the AMANDA and BAIKAL neutrino telescopes'' (with C.~Wiebusch {\it et al.}  [AMANDA and BAIKAL Collaboration]). Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 52B}, 256 (1997). %(Feb 1997)
%\href{http://inspirehep.net/record/439367}{HEP entry}


%{Miller:1996cd}
\item ``Particle astrophysics in antarctica'' (with T.~C.~Miller, P.~A.~Evenson, T.~K.~Gaisser, D.~Martello, G.~M.~Spiczak, T.~Stanev, E.~Dickinson and J.~R.~Gill {\it et al.}). In *Erice 1996, Towards the millennium in astrophysics* 157-166 %(1996)
%\href{http://inspirehep.net/record/433115}{HEP entry}


%{Jacobsen:1996ni}
\item ``Simulating the detection of muons and neutrinos in deep Antarctic ice'' (1996).
%\href{http://inspirehep.net/record/430516}{HEP entry}


%{Bergstrom:1996qs}
\item ``The AMANDA experiment: Status and prospects for indirect dark matter detection'' (with L.~Bergstrom {\it et al.}  [AMANDA Collaboration]). astro-ph/9612122
\\{}In *Sheffield 1996, The identification of dark matter* 521-528 %(Sep 1996)
%\href{http://inspirehep.net/record/427469}{HEP entry}


%{Hulth:1996tj}
\item ``The AMANDA experiment'' (with P.~O.~Hulth {\it et al.}  [AMANDA Collaboration]). astro-ph/9612068
\\{}In *Helsinki 1996, Neutrino physics and astrophysics* 518-523 %(Dec 1996)
%\href{http://inspirehep.net/record/427114}{HEP entry}


%{Askebjer:1995vm}
\item ``AMANDA: Status report from the 1993-94 campaign and optical properties of the South Pole ice'' (with P.~Askebjer {\it et al.}  [AMANDA Collaboration]). 10.1016/0920-5632(94)00757-M
\\{}Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 38}, 287 (1995). %(1995)
%\href{http://inspirehep.net/record/410087}{HEP entry}


%{Miller:1995jn}
\item ``Initial analysis of coincident events between the SPASE and AMANDA detectors'' (with T.~Miller {\it et al.}  [SPASE and AMANDA Collaboration]). 10.1016/0920-5632(95)00482-O
\\{}Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 43}, 245 (1995). %(1995)
%\href{http://inspirehep.net/record/410046}{HEP entry}


%{Halzen:1995ex}
\item ``Ultratransparent Antarctic ice as a supernova detector'' (with F.~Halzen and E.~Zas). astro-ph/9512080
    \\{}10.1103/PhysRevD.53.7359
\\{}Phys.\ Rev.\ D {\bf 53}, 7359 (1996) %(Dec 1995)
%\href{http://inspirehep.net/record/403544}{HEP entry}


%{Wischnewski:1995cu}
\item ``A System to search for supernova bursts with the AMANDA detector'' (with R.~Wischnewski {\it et al.}  [AMANDA Collaboration]). Preprint - Wischnewski, R. (95,rec.May) 4 p %(1995)
%\href{http://inspirehep.net/record/401781}{HEP entry}


%{Mock:1995ct}
\item ``Status and capabilities of AMANDA-94'' (with P.~C.~Mock {\it et al.}  [AMANDA Collaboration]). Preprint - Mock, P.C. (95,rec.May) 4 p %(1995)
%\href{http://inspirehep.net/record/401780}{HEP entry}


%{Erlandsson:1995cs}
\item ``Measurements of the absorption length of the ice at the South Pole in the wavelength interval 410-nm to 610-nm'' (with B.~Erlandsson {\it et al.}  [AMANDA Collaboration]). Preprint - Erlandsson, B. (95,rec.May) 4 p %(1995)
%\href{http://inspirehep.net/record/401779}{HEP entry}


%{Tilav:1995cr}
\item ``Indirect evidence for long absorption lengths in Antarctic ice'' (with S.~Tilav {\it et al.}  [AMANDA Collaboration]). Preprint - Tilav, S. (95,rec.May) 4 p %(1995)
%\href{http://inspirehep.net/record/401778}{HEP entry}


%{Gray:1995cq}
\item ``The Design of a neutrino telescope using natural deep ice as a particle detector'' (with L.~Gray {\it et al.}  [AMANDA Collaboration]). Preprint - Gray, L. (95,rec.May) 4 p %(1995)
%\href{http://inspirehep.net/record/401777}{HEP entry}


%{Askebjer:1995nx}
\item ``On the age versus depth and optical clarity of deep ice at South Pole'' (with P.~Askebjer {\it et al.}  [AMANDA Collaboration]). astro-ph/9501072
  
 %(Jan 1995)
%\href{http://inspirehep.net/record/392255}{HEP entry}


%{Price:1994ha}
\item ``Ultrahigh-energy neutrino astrophysics with AMANDA'' (with P.~B.~Price, A.~Goobar, D.~Lowder, T.~Miller, A.~Richards, A.~Westphal, S.~Barwick and J.~Lynch {\it et al.}.
  
 %(Jan 1994)
%\href{http://inspirehep.net/record/389458}{HEP entry}


%{Askebjer:1994yn}
\item ``Optical properties of the South Pole ice at depths between 0.8-km and 1-km'' (with P.~Askebjer {\it et al.}  [AMANDA Collaboration]). astro-ph/9412028
  \\{}Science {\bf 267}, 1147 (1995) %(Dec 1994)
%\href{http://inspirehep.net/record/381197}{HEP entry}


%{Halzen:1994xe}
\item ``Possibility that high-energy neutrino telescopes could detect supernovae'' (with F.~Halzen and E.~Zas). 10.1103/PhysRevD.49.1758
\\{}Phys.\ Rev.\ D {\bf 49}, 1758 (1994). %(1994)
%\href{http://inspirehep.net/record/377606}{HEP entry}


%{Halzen:1994ie}
\item ``The Detection of cold dark matter with neutrino telescopes'' (with F.~Halzen). hep-ph/9406309
  \\{}In *Montreal 1994, Proceedings, What next?* 97-112, and Wisconsin U. Madison - MAD-PH-838 (94/06,rec.Jun.) 26 p %(Jun 1994)
%\href{http://inspirehep.net/record/374110}{HEP entry}


%{Halzen:1994zq}
\item ``The Indirect detection of halo dark matter'' (with F.~Halzen). hep-ph/9404252
  
 %(Mar 1994)
%\href{http://inspirehep.net/record/372687}{HEP entry}


%{Barbagli:1993gz}
\item ``GASP: Gamma-ray astronomy at the South Pole'' (with G.~Barbagli {\it et al.}  [GASP Collaboration]). 
\\{}In *Calgary 1993, Towards a major atmospheric Cherenkov detector for TeV astro/particle physics* 72-74 %(1993)
%\href{http://inspirehep.net/record/367240}{HEP entry}


%{Morse:1993en}
\item ``The AMANDA neutrino astronomy project'' (with R.~Morse {\it et al.}  [AMANDA Collaboration]). In *Venice 1993, Neutrino telescopes* 309-320 %(1993)
%\href{http://inspirehep.net/record/366832}{HEP entry}


%{Halzen:1993vb}
\item ``High-energy neutrino telescopes detect supernovae'' (with F.~Halzen and E.~Zas). hep-ph/9307240
  
 %(Jun 1993)
%\href{http://inspirehep.net/record/356407}{HEP entry}


%{Halzen:1992fi}
\item ``Antarctic muon and neutrino detector array'' (with F.~Halzen, V.~Kandhadai, I.~Liubarsky, R.~Morse, S.~Tilav, S.~Barwick and J.~Lynch {\it et al.}). In *Venice 1992, Neutrino telescopes* 449-466 %(1992)
%\href{http://inspirehep.net/record/348335}{HEP entry}


%{Barwick:1992qz}
\item ``AMANDA: South pole neutrino detector'' (with S.~Barwick, J.~Lynch, R.~Porrata, G.~Yodh, D.~Lowder, T.~Miller, B.~Price and A.~Richards {\it et al.}). AIP Conf.\ Proc.\  {\bf 272}, 1250 (1993). %(Aug 1992)
%\href{http://inspirehep.net/record/338944}{HEP entry}


%{Barwick:1992cv}
\item ``Transparency of antartic ice: First results'' (with S.~W.~Barwick, J.~Lynch, R.~Porrata, G.~Yodh, D.~Lowder, T.~Miller, B.~Price and A.~Richards {\it et al.}). In *Honolulu 1992, High energy neutrino astrophysics* 291-308 %(Mar 1992)
%\href{http://inspirehep.net/record/338737}{HEP entry}


%{Barwick:1992rp}
\item ``Antarctic muon and neutrino detector array'' (with S.~W.~Barwick, J.~Lynch, R.~Porrata, G.~Yodh, D.~Lowder, T.~Miller, P.~B.~Price and A.~Richards {\it et al.}.
  
 %(Feb 1992)
%\href{http://inspirehep.net/record/337893}{HEP entry}


%{Decamp:1991di}
\item ``Measurement of the absolute luminosity with the ALEPH detector'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1007/BF01625896
\\{}Z.\ Phys.\ C {\bf 53}, 375 (1992). %(Aug 1991)
%\href{http://inspirehep.net/record/319668}{HEP entry}


%{Decamp:1991uz}
\item ``Measurement of the charged particle multiplicity distribution in hadronic Z decays'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)90575-B
\\{}Phys.\ Lett.\ B {\bf 273}, 181 (1991). %(Sep 1991)
%\href{http://inspirehep.net/record/319520}{HEP entry}


%{Decamp:1991uy}
\item ``Searches for new particles in $Z$ decays using the ALEPH detector'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-1573(92)90177-2
\\{}Phys.\ Rept.\  {\bf 216}, 253 (1992). %(Sep 1991)
%\href{http://inspirehep.net/record/319519}{HEP entry}


%{Decamp:1991jw}
\item ``Production and decay of charmed mesons at the Z resonance'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)90769-M
\\{}Phys.\ Lett.\ B {\bf 266}, 218 (1991). %(Jul 1991)
%\href{http://inspirehep.net/record/318149}{HEP entry}


%{Decamp:1991jr}
\item ``An Investigation into intermittency'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1007/BF01483869
\\{}Z.\ Phys.\ C {\bf 53}, 21 (1992). %(Jul 1991)
%\href{http://inspirehep.net/record/318145}{HEP entry}


%{Decamp:1991wi}
\item ``Search for the neutral Higgs bosons of the MSSM and other two doublet models'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)90083-3
\\{}Phys.\ Lett.\ B {\bf 265}, 475 (1991). %(Jul 1991)
%\href{http://inspirehep.net/record/317492}{HEP entry}


%{Decamp:1991aj}
\item ``Improved measurements of electroweak parameters from $Z$ decays into fermion pairs'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1007/BF01483868
\\{}Z.\ Phys.\ C {\bf 53}, 1 (1992). %(Jul 1991)
%\href{http://inspirehep.net/record/317141}{HEP entry}


%{Decamp:1991vz}
\item ``Measurement of the polarization of tau leptons produced in Z decays'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)90079-6
\\{}Phys.\ Lett.\ B {\bf 265}, 430 (1991). %(Jun 1991)
%\href{http://inspirehep.net/record/316781}{HEP entry}


%{Decamp:1991vy}
\item ``Measurement of isolated photon production in hadronic Z decays'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)90380-9
\\{}Phys.\ Lett.\ B {\bf 264}, 476 (1991). %(Jun 1991)
%\href{http://inspirehep.net/record/316780}{HEP entry}


%{Bellantoni:1991ei}
\item ``Using neural networks with jet shapes to identify b jets in e+ e- interactions'' (with L.~Bellantoni, J.~S.~Conway, Y.~B.~Pan and S.~L.~Wu). 10.1016/0168-9002(91)91108-8
\\{}Nucl.\ Instrum.\ Meth.\ A {\bf 310}, 618 (1991). %(May 1991)
%\href{http://inspirehep.net/record/316150}{HEP entry}


%{Decamp:1991eg}
\item ``Measurement of the forward - backward asymmetry in Z ---> b anti-b and Z ---> c anti-c'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)90607-R
\\{}Phys.\ Lett.\ B {\bf 263}, 325 (1991). %(Apr 1991)
%\href{http://inspirehep.net/record/316148}{HEP entry}


%{Decamp:1991sh}
\item ``Charged particle pair production associated with a lepton pair in Z decays: Indication of an excess in the tau channel'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)91716-9
\\{}Phys.\ Lett.\ B {\bf 263}, 112 (1991). %(Apr 1991)
%\href{http://inspirehep.net/record/315054}{HEP entry}


%{Decamp:1991bz}
\item ``Search for a new weakly interacting particle'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)90657-C
\\{}Phys.\ Lett.\ B {\bf 262}, 139 (1991). %(Feb 1991)
%\href{http://inspirehep.net/record/314875}{HEP entry}


%{Decamp:1991se}
\item ``Measurement of charge asymmetry in hadronic Z decays'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)90844-G
\\{}Phys.\ Lett.\ B {\bf 259}, 377 (1991). %(Feb 1991)
%\href{http://inspirehep.net/record/314476}{HEP entry}


%{Decamp:1991uj}
\item ``Searches for the standard Higgs boson produced in the reaction e+ e- ---> H0 Z*'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]).
  
 %(Jan 1991)
%\href{http://inspirehep.net/record/314056}{HEP entry}


%{Austin:1990vw}
\item ``TeV gamma-rays from Hercules X-1 at an anomalous period'' (with R.~Austin, U.~Camerini, J.~Finley, W.~Fry, J.~Gaidos, J.~Hudson, and J.~Jennings {\it et al.}). In *Adelaide 1990, Proceedings, Cosmic ray, vol. 2* 110-113 %(1990)
%\href{http://inspirehep.net/record/309005}{HEP entry}


%{Decamp:1990nf}
\item ``Measurement of alpha-s from the structure of particle clusters produced in hadronic Z decays'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)91926-M
\\{}Phys.\ Lett.\ B {\bf 257}, 479 (1991). %(Dec 1990)
%\href{http://inspirehep.net/record/302771}{HEP entry}


%{Decamp:1990ne}
\item ``Measurement of the B hadron lifetime'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)91927-N
\\{}Phys.\ Lett.\ B {\bf 257}, 492 (1991). %(Dec 1990)
%\href{http://inspirehep.net/record/302770}{HEP entry}


%{Decamp:1990nd}
\item ``Measurement of B - anti-B mixing at the Z'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)91239-R
\\{}Phys.\ Lett.\ B {\bf 258}, 236 (1991). %(Dec 1990)
%\href{http://inspirehep.net/record/302769}{HEP entry}


%{Decamp:1990cg}
\item ``Measurement of the strong coupling constant alpha-s from global event shape variables of hadronic Z decays'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(91)90278-X
\\{}Phys.\ Lett.\ B {\bf 255}, 623 (1991). %(Nov 1990)
%\href{http://inspirehep.net/record/301661}{HEP entry}


%{Decamp:1990sq}
\item ``Search for excited neutrinos in Z decay'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1016/0370-2693(90)91174-A
\\{}Phys.\ Lett.\ B {\bf 250}, 172 (1990). %(Aug 1990)
%\href{http://inspirehep.net/record/298839}{HEP entry}


%{Decamp:1990ky}
\item ``Measurement of electroweak parameters from Z decays into Fermion pairs'' (with D.~Decamp {\it et al.}  [ALEPH Collaboration]). 10.1007/BF01572019
\\{}Z.\ Phys.\ C {\bf 48}, 365 (1990). %(Jul 1990)
%\href{http://inspirehep.net/record/298414}{HEP entry}


%{Resvanis:1989my}
\item ``VHE gamma-ray studies at the Haleakala Gamma Observatory'' (with L.~K.~Resvanis, A.~Szentgyorgyi, M.~Kertzman, P.~Slane, J.~Hudson, L.~Kelley, J.~G.~Learned and C.~Sinnis {\it et al.}). Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 14A}, 205 (1990). %(1989)
%\href{http://inspirehep.net/record/291651}{HEP entry}

\end{enumerate}

\end{document}

